---
title: "Effects of self-compassion on PTG and PTST"
author: "[Corrado Caudek](https://ccaudek.github.io/)"
date: "First version 2020-01-12. Last modified `r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    toc: true
    number_sections: false
    fig_caption: true
---

# Aim

Compute the partial correlations as in Table 1 of Muris, Otgaar & Pfattheicher (2019).


# Prelims

```{r prelims, echo=FALSE}
library("here")
suppressPackageStartupMessages(library("lavaan"))
suppressPackageStartupMessages(library("tidyverse"))
suppressPackageStartupMessages(library("ggthemes"))
suppressPackageStartupMessages(library("tidyverse"))
suppressPackageStartupMessages(library("tidyr"))
suppressPackageStartupMessages(library("mice"))
suppressPackageStartupMessages(library("corrplot"))
suppressPackageStartupMessages(library("bayesplot"))
suppressPackageStartupMessages(library("nonnest2"))
suppressPackageStartupMessages(library("semPlot"))
suppressPackageStartupMessages(library("ppcor"))


theme_set(bayesplot::theme_default(base_family = "sans", base_size=14))
options(max.print = 99999999)
```

```{r, echo=FALSE}
# Functions
source(here("libraries", "self_compassion_fnc.R"))
```

```{r read_data}
# Read data
temp <- read.csv(
  file = here("data", "processed", "rescue_workers.csv"),
  header = TRUE,
  sep = ";"
)
```

```{r wrangling, warning=FALSE, message=FALSE, echo=FALSE}
# Data wrangling

# remove uninformative variable
temp$is_rescue_worker <- NULL

# remove missing data on all questionnaires data (for convenience,
# I use the variable 'friends')
mydata <- temp[!is.na(temp$friends), ]
# summary(mydata)

# Multiple imputation 

# MI for age.
# select only the numeric columns of 'temp1'
nums <- unlist(lapply(mydata, is.numeric))
dat_num <- mydata[, nums]

# one value of 'years_experience' is miscoded: 2011;
# it will be recoded as NA and the multiply imputed and
# added again to the 'mydata' data.frame
dat_num$years_experience <- ifelse(
  dat_num$years_experience == 2011, NA, dat_num$years_experience
)

imp <- mice(
  dat_num,
  method = "midastouch",
  m = 1,
  maxit = 1,
  seed = 12345
)

d_imp <- complete(imp)
# summary(dat_num$age)
# summary(d_imp$age)

# add imputed 'age' to mydata
mydata$age_imp <- d_imp$age
mydata$years_experience <- d_imp$years_experience

# mydata$life_appreciation <- d_imp$life_appreciation
# mydata$new_possibilities <- d_imp$new_possibilities
# mydata$personal_strength <- d_imp$personal_strength
# mydata$spirituality_changes <- d_imp$spirituality_changes
# mydata$interpersonal_relationships <- d_imp$interpersonal_relationships

if (0) ggplot(data = mydata, aes(new_possibilities)) +
  geom_histogram(
    aes(y = ..density..),
    # breaks=seq(0, 85, by = 2),
    col = "red",
    fill = "green",
    alpha = .2
  ) +
  geom_density(col = 2)

# mydata$ptg <- mydata$life_appreciation + mydata$new_possibilities +
#   mydata$personal_strength + mydata$spirituality_changes +
#   mydata$interpersonal_relationships

rm(d_imp, dat_num, temp)

# Data wrangling 

# Compute total score for MSPSS
mydata$mspss <- mydata$family + mydata$friends + mydata$significant_other

# Recode rate of activity as a numeric variable
mydata$activity_rate <- as.numeric(
  as.character(fct_recode(
    mydata$rate_of_activity,
    "5" = "Pi첫 di 1 turno a settimana",
    "4" = "1 turno a settimana",
    "3" = "1 turno ogni due settimane",
    "2" = "1 turno al mese",
    "1" = "Meno di 1 turno al mese"
  ))
)

# Recode education as a numeric variable
mydata$edu <- as.numeric(
  as.character(fct_recode(
    mydata$education,
    "1" = "Scuola media primaria",
    "2" = "Diploma",
    "3" = "Laurea breve",
    "4" = "Laurea magistrale",
    "5" = "Dottorato"
  ))
)

# Recode last_training as a numeric variable
mydata$training_time <- as.numeric(
  as.character(fct_recode(
    mydata$last_training,
    "1" = "Meno di 2 mesi fa",
    "2" = "Pi첫 di 2 mesi fa",
    "3" = "Meno di 6 mesi fa",
    "4" = "Pi첫 di 6 mesi fa",
    "5" = "Meno di 1 anno fa",
    "6" = "Pi첫 di 1 anno fa"
  ))
)

mydata$job_qualification <- fct_recode(
  mydata$job_qualification,
  "Soccorritore" = "Infermiere",
  "Soccorritore" = "Medico"
)

df <- mydata %>%
  drop_na(ptg)

df <- df %>%
  mutate(
    spirituality_changes = spirituality_changes * 3
  )

df <- df %>% 
  dplyr::rename_all(
    dplyr::recode, 
    avoiding = "avoidance",
    intrusivity = "intrusion",
    iperarousal = "hyperarousal"
)
```


```{r}
df$ptss <- df$avoidance + df$intrusion + df$hyperarousal
df$nsc <-  df$self_judgment + df$isolation + df$over_identification
df$psc <- df$self_kindness + df$common_humanity + df$mindfulness
```



```{r}
mydata <- data.frame(
  # neuroticism = df$neuroticism,
  negative_affect = df$negative_affect,
  self_reproach = df$self_reproach,
  ptg = df$ptg,
  ptss = df$ptss, 
  nsc = df$nsc,
  psc = df$psc
)
```


# Partial correlations

```{r}
print(cor(mydata), 2)
```

```{r}
ppcor::pcor(mydata)
```


Partial correlation between negative affect and nsc, given psc:
```{r}
fm1 <- lm(negative_affect ~ psc, data = df)
fm2 <- lm(nsc ~ psc, data = df)
cor.test(fm1$res, fm2$res)
```

Partial correlation between negative affect and psc, given nsc:
```{r}
fm3 <- lm(negative_affect ~ nsc, data = df)
fm4 <- lm(psc ~ nsc, data = df)
cor.test(fm3$res, fm4$res)
```


Partial correlation between self reproach and nsc, given psc:
```{r}
fm5 <- lm(self_reproach ~ psc, data = df)
fm6 <- lm(nsc ~ psc, data = df)
cor.test(fm5$res, fm6$res)
```

Partial correlation between self reproach and psc, given nsc:
```{r}
fm7 <- lm(self_reproach ~ nsc, data = df)
fm8 <- lm(psc ~ nsc, data = df)
cor.test(fm7$res, fm8$res)
```



Partial correlation between ptss and nsc, given psc:
```{r}
fm9 <- lm(ptss ~ psc, data = df)
fm10 <- lm(nsc ~ psc, data = df)
cor.test(fm9$res, fm10$res)
```

Partial correlation between ptss and psc, given nsc:
```{r}
fm11 <- lm(ptss ~ nsc, data = df)
fm12 <- lm(psc ~ nsc, data = df)
cor.test(fm11$res, fm12$res)
```


Partial correlation between ptg and nsc, given psc:
```{r}
fm13 <- lm(ptg ~ psc, data = df)
fm14 <- lm(nsc ~ psc, data = df)
cor.test(fm13$res, fm14$res)
```

Partial correlation between ptg and psc, given nsc:
```{r}
fm15 <- lm(ptg ~ nsc, data = df)
fm16 <- lm(psc ~ nsc, data = df)
cor.test(fm15$res, fm16$res)
```



Partial correlation between mpss and nsc, given psc:
```{r}
fm17 <- lm(mspss ~ psc, data = df)
fm18 <- lm(nsc ~ psc, data = df)
cor.test(fm17$res, fm18$res)
```


Partial correlation between mpss and psc, given nsc:
```{r}
fm19 <- lm(mspss ~ nsc, data = df)
fm20 <- lm(psc ~ nsc, data = df)
cor.test(fm19$res, fm20$res)
```









