---
title: "Summary statistics and mediational models"
subtitle: "Self-compassion project"
author: "[Corrado Caudek](https://ccaudek.github.io/)"
date: "First version 2020-01-12. Last modified `r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    toc: true
    number_sections: false
    fig_caption: true
---

# Aim

Compute the summary statistics of the sample used in the self-compassion project.


# Prelims

```{r prelims, echo=FALSE}
library("here")
suppressPackageStartupMessages(library("lavaan"))
suppressPackageStartupMessages(library("tidyverse"))
suppressPackageStartupMessages(library("ggthemes"))
suppressPackageStartupMessages(library("tidyverse"))
suppressPackageStartupMessages(library("tidyr"))
suppressPackageStartupMessages(library("mice"))
suppressPackageStartupMessages(library("corrplot"))
suppressPackageStartupMessages(library("bayesplot"))
suppressPackageStartupMessages(library("nonnest2"))
suppressPackageStartupMessages(library("semPlot"))
suppressPackageStartupMessages(library("ppcor"))
suppressPackageStartupMessages(library("skimr"))

theme_set(bayesplot::theme_default(base_family = "sans", base_size=14))
options(max.print = 99999999)
```

```{r, echo=FALSE}
# Functions
source(here("libraries", "self_compassion_fnc.R"))
```

```{r read_data}
# Read data
temp <- read.csv(
  file = here("data", "processed", "rescue_workers.csv"),
  header = TRUE,
  sep = ";"
)
```

```{r wrangling, warning=FALSE, message=FALSE, echo=FALSE}
# Data wrangling

# remove uninformative variable
temp$is_rescue_worker <- NULL

# remove missing data on all questionnaires data (for convenience,
# I use the variable 'friends')
mydata <- temp[!is.na(temp$friends), ]
# summary(mydata)

# Multiple imputation 

# MI for age.
# select only the numeric columns of 'temp1'
nums <- unlist(lapply(mydata, is.numeric))
dat_num <- mydata[, nums]

# one value of 'years_experience' is miscoded: 2011;
# it will be recoded as NA and the multiply imputed and
# added again to the 'mydata' data.frame
dat_num$years_experience <- ifelse(
  dat_num$years_experience == 2011, NA, dat_num$years_experience
)

imp <- mice(
  dat_num,
  method = "midastouch",
  m = 1,
  maxit = 1,
  seed = 12345
)

d_imp <- complete(imp)
# summary(dat_num$age)
# summary(d_imp$age)

# add imputed 'age' to mydata
mydata$age_imp <- d_imp$age
mydata$years_experience <- d_imp$years_experience

# mydata$life_appreciation <- d_imp$life_appreciation
# mydata$new_possibilities <- d_imp$new_possibilities
# mydata$personal_strength <- d_imp$personal_strength
# mydata$spirituality_changes <- d_imp$spirituality_changes
# mydata$interpersonal_relationships <- d_imp$interpersonal_relationships

if (0) ggplot(data = mydata, aes(new_possibilities)) +
  geom_histogram(
    aes(y = ..density..),
    # breaks=seq(0, 85, by = 2),
    col = "red",
    fill = "green",
    alpha = .2
  ) +
  geom_density(col = 2)

# mydata$ptg <- mydata$life_appreciation + mydata$new_possibilities +
#   mydata$personal_strength + mydata$spirituality_changes +
#   mydata$interpersonal_relationships

rm(d_imp, dat_num, temp)

# Data wrangling 

# Compute total score for MSPSS
mydata$mspss <- mydata$family + mydata$friends + mydata$significant_other

# Recode rate of activity as a numeric variable
mydata$activity_rate <- as.numeric(
  as.character(fct_recode(
    mydata$rate_of_activity,
    "5" = "Più di 1 turno a settimana",
    "4" = "1 turno a settimana",
    "3" = "1 turno ogni due settimane",
    "2" = "1 turno al mese",
    "1" = "Meno di 1 turno al mese"
  ))
)

# Recode education as a numeric variable
mydata$edu <- as.numeric(
  as.character(fct_recode(
    mydata$education,
    "1" = "Scuola media primaria",
    "2" = "Diploma",
    "3" = "Laurea breve",
    "4" = "Laurea magistrale",
    "5" = "Dottorato"
  ))
)

# Recode last_training as a numeric variable
mydata$training_time <- as.numeric(
  as.character(fct_recode(
    mydata$last_training,
    "1" = "Meno di 2 mesi fa",
    "2" = "Più di 2 mesi fa",
    "3" = "Meno di 6 mesi fa",
    "4" = "Più di 6 mesi fa",
    "5" = "Meno di 1 anno fa",
    "6" = "Più di 1 anno fa"
  ))
)

mydata$job_qualification <- fct_recode(
  mydata$job_qualification,
  "Soccorritore" = "Infermiere",
  "Soccorritore" = "Medico"
)

df <- mydata %>%
  drop_na(ptg)

df <- df %>%
  mutate(
    spirituality_changes = spirituality_changes * 3
  )

df <- df %>% 
  dplyr::rename_all(
    dplyr::recode, 
    avoiding = "avoidance",
    intrusivity = "intrusion",
    iperarousal = "hyperarousal"
)
```


```{r}
df$ptss <- df$avoidance + df$intrusion + df$hyperarousal
df$nsc <-  df$self_judgment + df$isolation + df$over_identification
df$psc <- df$self_kindness + df$common_humanity + df$mindfulness
```



```{r}
thedat <- data.frame(
  # neuroticism = df$neuroticism,
  negative_affect = df$negative_affect,
  self_reproach = df$self_reproach,
  ptg = df$ptg,
  ptss = df$ptss, 
  nsc = df$nsc,
  psc = df$psc
)
```


# Correlations

Winders et al. (2020) reports that 

> of the studies that reported correlational data about the relationship between self-compassion and PTSD (defined using DSM-IV or DSM-5 criteria; n = 14), five reported a strong, significant negative relationship, six studies reported a moderate, significant negative relationship and two a weak, significant negative relationship. Only one study reported no significant relationship.

```{r}
print(cor(thedat), 2)
```

There is a negative correlation between Negative Self-Compassion and IES-R; no correlation between IES-R and the positive component of self-compassion.

```{r}
cor.test(thedat$ptss, thedat$nsc)
```


```{r}
cor.test(thedat$ptss, thedat$psc)
```


# PTSD: Mediational models with coping as a mediating variable


> Ten of the papers employed mediational analysis to explore the relationships between self-compassion, trauma and PTSD. One study found a significant direct relationship between self-compassion and PTSD (Bistricky et al., 2017) and four studies found indirect relationships via interpersonal competence (Bistricky et al., 2017), emotional dysregulation (Barlow et al., 2017), self‐blame attributions and disengagement coping (Hamrick & Owens, 2018) and grief ruminations (Lenferink et al., 2017). -- Winders et al. (2020)

```{r}
mediation_an_1 <- function(d) {
  
  set.seed(1234)
  
  d <- d %>% 
    dplyr::rename(
      X = x,
      Y = y,
      M = m
    )
  
  mediation_model <- ' 
    # direct effect
    Y ~ c*X
    
    # mediator
    M ~ a*X
    Y ~ b*M
    
    # indirect effect (a*b)
    ab := a*b
    
    # total effect
    total := c + (a*b)
  '
  
  fit <- sem(mediation_model, data = d)
  fit
}
```


## Negative self-compassion

```{r}
d <- data.frame(
  x = df$nsc, 
  m = df$cope_nvi,  # df$positive_attitude + df$problem_orientation,  
  y = df$ptss
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```

## Positive self-compassion


```{r}
d <- data.frame(
  x = df$psc, 
  m = df$cope_nvi, 
  y = df$ptss
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```


# PTSD: Mediational models with self-compassion as a mediating variable


```{r}
d <- data.frame(
  x = df$cope_nvi, 
  m = df$nsc,    
  y = df$ptss
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```


```{r}
d <- data.frame(
  x = df$cope_nvi, 
  m = df$psc,    
  y = df$ptss
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```


# PTSD: Self-compassion and social support

> Some studies also looked at the mediating effects of self-compassion, finding that it partially mediated relationships between: social support and PTSD (Maheux & Price, 2016)


## Negative self-compassion

```{r}
d <- data.frame(
  x = df$social_support, 
  m = df$nsc,    
  y = df$ptss
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```

## Positive self-compassion

```{r}
d <- data.frame(
  x = df$social_support, 
  m = df$psc,    
  y = df$ptss
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```



# PTG: Mediational models with coping as a mediating variable


## Negative self-compassion

```{r}
d <- data.frame(
  x = df$nsc, 
  m = df$cope_nvi,  # df$positive_attitude + df$problem_orientation,  
  y = df$ptg
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```

## Positive self-compassion


```{r}
d <- data.frame(
  x = df$psc, 
  m = df$cope_nvi, 
  y = df$ptg
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```


# PTG: Mediational models with self-compassion as a mediating variable


```{r}
d <- data.frame(
  x = df$cope_nvi, 
  m = df$nsc,    
  y = df$ptg
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```


```{r}
d <- data.frame(
  x = df$cope_nvi, 
  m = df$psc,    
  y = df$ptg
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```


# PTG: Self-compassion and social support


## Negative self-compassion

```{r}
d <- data.frame(
  x = df$social_support, 
  m = df$nsc,    
  y = df$ptg
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```

## Positive self-compassion

```{r}
d <- data.frame(
  x = df$social_support, 
  m = df$psc,    
  y = df$ptg
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```








# Add Nevroticism to the previous models

```{r}
# W: Neuroticism
mediation_an_2 <- function(d) {
  
  set.seed(1234)
  
  d <- d %>% 
    dplyr::rename(
      X = x,
      Y = y,
      W = w,
      M = m
    )
  
  mediation_model <- ' 
    # direct effect
    Y ~ c*X
    Y ~ d*W
    
    # mediator
    M ~ a*X
    Y ~ b*M
    M ~ e*W
    
    # indirect effect (a*b)
    ab := a*b 
    eb := e*b
    
    # total effect
    total := c + (a*b) 
    total2 := d + (e*b)
    
  '
  
  fit <- sem(mediation_model, data = d)
  fit
}
```

## Negative self-compassion and Neuroticism

```{r}
d <- data.frame(
  x = df$nsc, 
  w = df$neuroticism,
  m = df$cope_nvi,  # df$positive_attitude + df$problem_orientation,  
  y = df$ptss
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_2(d)
summary(m)
```

## Positive self-compassion and Neuroticism

```{r}
d <- data.frame(
  x = df$psc, 
  w = df$neuroticism,
  m = df$cope_nvi,  # df$positive_attitude + df$problem_orientation,  
  y = df$ptss
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_2(d)
summary(m)
```





```{r}

M5 <- ' 

  # ptsd
  ptss =~ NA*avoidance + intrusion + hyperarousal
  
  # post-traumatic growth
  ptg =~ NA*life_appreciation + new_possibilities + 
         personal_strength + spirituality_changes + 
         interpersonal_relationships
         
  # self-compassion
  nsc =~ NA*self_judgment + isolation + over_identification
  psc =~ NA*self_kindness + common_humanity + mindfulness
  
  # neuroticism
  neuroticism =~ NA*negative_affect + self_reproach
  
  # variances
  ptg ~~ 1* ptg
  psc ~~ 1* psc
  nsc ~~ 1* nsc
  neuroticism ~~ 1* neuroticism
  ptss ~~ 1* ptss
  
  # regression
  ptg  ~ NA*avoiding_strategies + positive_attitude + problem_orientation + nsc + psc + neuroticism
  ptss ~ NA*avoiding_strategies + positive_attitude + problem_orientation + nsc + psc + neuroticism
  avoiding_strategies ~ NA*psc + nsc + neuroticism
  positive_attitude   ~ NA*psc + nsc + neuroticism
  problem_orientation ~ NA*psc + nsc + neuroticism
  
'
```

```{r}
fit5 <- lavaan::sem(
  M5,
  data = df
)
```


```{r}
summary(
  fit5,
  standardized = TRUE,
  fit.measures = TRUE,
  rsquare = TRUE
)
```

```{r}
fitMeasures(fit5, c("chisq", "df", "cfi", "tli", "rmsea", "srmr"))
```






