---
title: "Effects of self-compassion on Coping"
author: "[Corrado Caudek](https://ccaudek.github.io/)"
date: "First version 2020-01-12. Last modified `r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    toc: true
    number_sections: false
    fig_caption: true
---

# Aim

By following Chishima et al. (2018), evaluate models with the five components of COPE as endogenous variables, with Self-Compassion and Neuroticism as causal sources.


# Prelims

```{r prelims, echo=FALSE}
library("here")
suppressPackageStartupMessages(library("lavaan"))
suppressPackageStartupMessages(library("tidyverse"))
suppressPackageStartupMessages(library("ggthemes"))
suppressPackageStartupMessages(library("tidyverse"))
suppressPackageStartupMessages(library("tidyr"))
suppressPackageStartupMessages(library("mice"))
suppressPackageStartupMessages(library("corrplot"))
suppressPackageStartupMessages(library("bayesplot"))
suppressPackageStartupMessages(library("nonnest2"))
suppressPackageStartupMessages(library("semPlot"))

theme_set(bayesplot::theme_default(base_family = "sans", base_size=14))
options(max.print = 99999999)
```

```{r, echo=FALSE}
# Functions
source(here("libraries", "self_compassion_fnc.R"))
```

```{r read_data}
# Read data
temp <- read.csv(
  file = here("data", "processed", "rescue_workers.csv"),
  header = TRUE,
  sep = ";"
)
```

```{r wrangling, warning=FALSE, message=FALSE, echo=FALSE}
# Data wrangling

# remove uninformative variable
temp$is_rescue_worker <- NULL

# remove missing data on all questionnaires data (for convenience,
# I use the variable 'friends')
mydata <- temp[!is.na(temp$friends), ]
# summary(mydata)

# Multiple imputation 

# MI for age.
# select only the numeric columns of 'temp1'
nums <- unlist(lapply(mydata, is.numeric))
dat_num <- mydata[, nums]

# one value of 'years_experience' is miscoded: 2011;
# it will be recoded as NA and the multiply imputed and
# added again to the 'mydata' data.frame
dat_num$years_experience <- ifelse(
  dat_num$years_experience == 2011, NA, dat_num$years_experience
)

imp <- mice(
  dat_num,
  method = "midastouch",
  m = 1,
  maxit = 1,
  seed = 12345
)

d_imp <- complete(imp)
# summary(dat_num$age)
# summary(d_imp$age)

# add imputed 'age' to mydata
mydata$age_imp <- d_imp$age
mydata$years_experience <- d_imp$years_experience

# mydata$life_appreciation <- d_imp$life_appreciation
# mydata$new_possibilities <- d_imp$new_possibilities
# mydata$personal_strength <- d_imp$personal_strength
# mydata$spirituality_changes <- d_imp$spirituality_changes
# mydata$interpersonal_relationships <- d_imp$interpersonal_relationships

if (0) ggplot(data = mydata, aes(new_possibilities)) +
  geom_histogram(
    aes(y = ..density..),
    # breaks=seq(0, 85, by = 2),
    col = "red",
    fill = "green",
    alpha = .2
  ) +
  geom_density(col = 2)

# mydata$ptg <- mydata$life_appreciation + mydata$new_possibilities +
#   mydata$personal_strength + mydata$spirituality_changes +
#   mydata$interpersonal_relationships

rm(d_imp, dat_num, temp)

# Data wrangling 

# Compute total score for MSPSS
mydata$mspss <- mydata$family + mydata$friends + mydata$significant_other

# Recode rate of activity as a numeric variable
mydata$activity_rate <- as.numeric(
  as.character(fct_recode(
    mydata$rate_of_activity,
    "5" = "Pi첫 di 1 turno a settimana",
    "4" = "1 turno a settimana",
    "3" = "1 turno ogni due settimane",
    "2" = "1 turno al mese",
    "1" = "Meno di 1 turno al mese"
  ))
)

# Recode education as a numeric variable
mydata$edu <- as.numeric(
  as.character(fct_recode(
    mydata$education,
    "1" = "Scuola media primaria",
    "2" = "Diploma",
    "3" = "Laurea breve",
    "4" = "Laurea magistrale",
    "5" = "Dottorato"
  ))
)

# Recode last_training as a numeric variable
mydata$training_time <- as.numeric(
  as.character(fct_recode(
    mydata$last_training,
    "1" = "Meno di 2 mesi fa",
    "2" = "Pi첫 di 2 mesi fa",
    "3" = "Meno di 6 mesi fa",
    "4" = "Pi첫 di 6 mesi fa",
    "5" = "Meno di 1 anno fa",
    "6" = "Pi첫 di 1 anno fa"
  ))
)

mydata$job_qualification <- fct_recode(
  mydata$job_qualification,
  "Soccorritore" = "Infermiere",
  "Soccorritore" = "Medico"
)

df <- mydata %>%
  drop_na(ptg)

df <- df %>%
  mutate(
    spirituality_changes = spirituality_changes * 3
  )

df <- df %>% 
  dplyr::rename_all(
    dplyr::recode, 
    avoiding = "avoidance",
    intrusivity = "intrusion",
    iperarousal = "hyperarousal"
)
```


# Check for outliers

```{r}
tmp <- df %>%
  dplyr::select(
    life_appreciation, new_possibilities,
    personal_strength, spirituality_changes,
    interpersonal_relationships,
    avoidance, intrusion, hyperarousal,
    social_support, avoiding_strategies,
    positive_attitude, problem_orientation,
    transcendent_orientation,
    family, friends, significant_other,
    self_judgment, isolation, over_identification,
    self_kindness, common_humanity, mindfulness
  )

d2mydata <- psych::outlier(tmp, cex=.6, bad=5)
```

Remove 1 extreme observation.

```{r}
df <- df[-c(680), ]
```




# Model 1


M1 distinguishes between the two (correlated) components of self-compassion: positive and negative self-compassion.

```{r}
M1 <- "

  # neuroticism
  neuroticism =~ NA*negative_affect + self_reproach
  
  # coping
  cope =~ NA*positive_attitude + problem_orientation + avoiding_strategies 
          # transcendent_orientation + social_support
  
  # self-compassion
  nsc =~ NA*self_judgment + isolation + over_identification
  psc =~ NA*self_kindness + common_humanity + mindfulness
  
  # regressions
  cope ~ nsc + psc + neuroticism
  
  # fix variance of latent factors
  cope ~~ 1*cope
  nsc  ~~ 1*nsc
  psc  ~~ 1*psc
  neuroticism ~~ 1*neuroticism
  
  # covariances
  psc ~~ nsc
  self_judgment ~~ self_kindness
"
```

Fit of M1.
```{r}
fit1 <- lavaan::sem(
  M1,
  data = df
)
```

```{r}
fitMeasures(fit1, c("chisq", "df", "cfi", "tli", "rmsea", "srmr"))
```

Fit is not adequate.


# Model 2

M2 considers as endogenous variable all the five components of COPE.

```{r}
M2 <- "

  # neuroticism
  neuroticism =~ NA*negative_affect + self_reproach

  # self-compassion
  nsc =~ NA*self_judgment + isolation + over_identification
  psc =~ NA*self_kindness + common_humanity + mindfulness

  # regressions
  positive_attitude ~ nsc + psc + neuroticism
  problem_orientation ~ nsc + psc + neuroticism
  social_support ~ nsc + psc + neuroticism
  # avoiding_strategies ~ nsc + psc + neuroticism
  # transcendent_orientation ~ nsc + psc + neuroticism
  
  # fix variance of latent factors
  nsc  ~~ 1*nsc
  psc  ~~ 1*psc
  neuroticism ~~ 1*neuroticism
  
  # covariances
  psc ~~ nsc
  self_judgment ~~ self_kindness
"
```

Fit of M2.

```{r}
fit2 <- lavaan::sem(
  M2,
  data = df
)
```

The fit improves: 

```{r}
vuongtest(fit3, fit5)
```

```{r}
semPaths(
  fit2, 
  curvePivot = FALSE, 
  what = "std", 
  title = FALSE, 
  residuals = FALSE
)
```

```{r}
summary(
  fit2,
  standardized = TRUE,
  fit.measures = TRUE,
  rsquare = TRUE
)
```

```{r}
fitMeasures(fit2, c("chisq", "df", "cfi", "tli", "rmsea", "srmr"))
```



# Conclusions

The fit of these models is bad.



