---
title: "Emergency psychology"
author: "[Corrado Caudek](https://ccaudek.github.io/)"
date: "First version 2019-02-14. Last modified `r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    fig_caption: yes
    highlight: pygments
    toc: TRUE
    toc_depth: 2
    number_sections: TRUE
    toc_float:
      smooth_scroll: FALSE
---

# Set up
```{r setup, include=FALSE}
suppressPackageStartupMessages(library("here"))
```


## Packages
```{r}
suppressPackageStartupMessages(library("googlesheets"))
suppressPackageStartupMessages(library("tidyverse"))
suppressPackageStartupMessages(library("lavaan"))
suppressPackageStartupMessages(library("mice"))  
```

Which google sheets do you have access to?
```{r}
# gs_ls()
```

Get the google sheet
```{r}
thedat <- gs_title("Sei un soccorritore in Emergenza? (Risposte)")
```

List worksheets
```{r}
gs_ws_ls(thedat)
```

Get data and convert to data.frame
```{r}
dat <- gs_read(ss=thedat, ws = "Risposte del modulo 1", skip=1)
df <- as.data.frame(dat)
```

Rename variables
```{r}
df <- df %>% 
  rename(
    date = `Informazioni cronologiche`,
    permission = `Trattamento dei dati personali`,
    id = `Inserisci il codice identificativo come sopra indicato:`,
    gender = Sesso,
    education = `Livello istruzione`,
    employment =  Occupazione,
    is_rescue_worker = `Sei un Soccorritore in Emergenza?`,
    red_cross_commeetee_location =  `Comitato Croce Rossa Italiana di appartenenza (per es. Comitato di Firenze)`,
    rescue_worker_qualification =  `Possiedi la qualifica TSSA/PTSI?`, 
    last_training = `Quando hai effettuato l'ultimo re-training, corso, inerente la qualifica TSSA/FULL-D?`,
    rate_of_activity =  `Con quale frequenza fai turno in Ambulanza?`,
    job_qualification =  `Generalmente fai turno sempre con la stessa squadra?`,
    is_job_qualification_invariant= `Generalmente fai turno sempre con la stessa squadra?`,
    age =  X231,
  ) 
```

The data.frame contains the following scales:

- NEO_FFI_60: 60 items, from X16 to X75. The NEO-FFI is a 60-item psychological personality inventory that assesses based on the five-factor model: Openness to Experience, Conscientiousness, Extraversion, Agreeableness, and Neuroticism. Participants are asked to select the response that best represents their opinion on a 5-point scale: 0-Strongly Agree, 1-Agree, 2-Neutral, 3-Disagree, 4-Strongly Disagree.

- COPE_NVI: 60 items, from X76 to X135. (Coping Orientation to Problems Experienced-Nuova Versione Italiana (COPE-NVI). The COPE-New Italian Version (COPE-NIV) represents an improvement of the previous Italian version of the COPE. La prima valutazione condotta è basata sulla media del punteggio totale del COPE-NVI. Tale punteggio è inteso come la somma dei punteggi attribuiti dai singoli rispondenti alle 60 domande. Il punteggio complessivo può essere considerato un indice di quanto la persona reagisca allo stress: maggiore è il punteggio, maggiore è il benessere psicologico di fronte a situazioni stressanti. Cinque dimensioni: Orientamento al problema, Attitudine positiva, Sostegno sociale, Evitamento, Orientamento trascendente.

- PTGI: 29 items, X136 to X143, X144 to X164. The Posttraumatic Growth Inventory was developed to assess positive outcomes in response totraumatic events. Five factors: Factor I: Relating to Others, Factor II: New Possibilities, Factor III: Personal Strength, Factor IV: Spiritual Change, and Factor V: Appreciation for Life.

- IES_R: 28 items, items X165 to X170, X171 to X192 (Impact of Event Scale - Revised). The IES-R is a 22-item self-report measure (for DSM-IV) that assesses subjective distress caused by traumatic events. It is a revised version of the older version, the 15-item IES (Horowitz, Wilner, & Alvarez, 1979). The IES-R contains seven additional items related to the hyperarousal symptoms of PTSD, which were not included in the original IES. Items correspond directly to 14 of the 17 DSM-IV symptoms of PTSD. Respondents are asked to identify a specific stressful life event and then indicate how much they were distressed or bothered during the past seven days by each "difficulty" listed. Items are rated on a 5-point scale ranging from 0 ("not at all") to 4 ("extremely"). The IES-R yields a total score (ranging from 0 to 88) and subscale scores can also be calculated for the Intrusion, Avoidance, and Hyperarousal subscales.

- SCS: 26 items, items X193 to 218. The  SCS (Neff,  2003a) is a 26-item  self-report  questionnaire measuring the six components of self-compassion: Self-Kindness(5 items; e.g., “I try to be loving towards myself when I’m feelingemotional pain”), reduced Self-Judgment (5 items; e.g., “I’m dis-approving  and  judgmental  about  my  own  flaws  and  inadequa-cies”), Common Humanity (4 items, e.g., “When things are goingbadly for me, I see the difficulties as part of life that everyone goesthrough”), reduced Isolation (4 items, e.g., “When I think about myinadequacies it tends to make me feel more separate and cut offfrom the rest of the world”), Mindfulness (4 items, e.g., “When I’mfeeling  down  I  try  to  approach  my  feelings  with  curiosity  andopenness”), and reduced Overidentification (4 items, e.g., “Whensomething upsets me I get carried away with my feelings”).

- MSPSS: 12 items, items X219 to 230 (Multidimensional Scale of Perceived Social Support, MSPSS). The MSPSS is a short instrument designed to measure an individual’s perception of support from 3 sources: family, friends and a significant other. To calculate total score: Sum across all 12 items. This total score can also be calculated as a mean score (divide by 12). To calculate the mean subscale scores:
Significant Other Subscale: Sum across items 1, 2, 5, & 10, then divide by 4.
Family Subscale: Sum across items 3, 4, 8, & 11, then divide by 4.
Friends Subscale: Sum across items 6, 7, 9, & 12, then divide by 4.



# Scala neo_ffi_60

Let start with the coding of neo_ffi_60. First, we select the right columns:
```{r}
neo_ffi_60 <- df %>% 
  select(X16:X75)
```

Then we change the column names to facilitate coding
```{r}
item_names <- paste0("i", 1:60)
names(neo_ffi_60) <- item_names
```

Some items are reversed. In that cases, we can compute the right value by using the following formula: abs(x - max).

The first factor of neo_ffi_60 is called neutoticism and is composed by two subscales. The scores on such scales are the following:

```{r}
negative_affect <- 
  abs(neo_ffi_60$i1 - 4) + neo_ffi_60$i11 + abs(neo_ffi_60$i16 - 4) + 
  abs(neo_ffi_60$i31 - 4) + abs(neo_ffi_60$i46 - 4)
```



```{r}
self_reproach <-
neo_ffi_60$i6 + neo_ffi_60$i21 + neo_ffi_60$i26 + neo_ffi_60$i36 + neo_ffi_60$i41 + neo_ffi_60$i51 + neo_ffi_60$i56
```

```{r}
neuroticism <- negative_affect + self_reproach
```

Just to take a look to the data, an histogram of neuroticism is
```{r}
hist(neuroticism)
```


The second factor of neo_ffi_60 is called extraversion and is composed by three subscales. The scores on such scales are the following:
```{r}
positive_affect <-
neo_ffi_60$i7 + abs(neo_ffi_60$i12 - 4) + neo_ffi_60$i37
 + abs(neo_ffi_60$i42 - 4)
```


```{r}
sociability <- 
neo_ffi_60$i2 + neo_ffi_60$i17 + abs(neo_ffi_60$i27 - 4) + abs(neo_ffi_60$i57 - 4)
```


```{r}
activity <- 
neo_ffi_60$i22 + neo_ffi_60$i32 + neo_ffi_60$i47 + neo_ffi_60$i52
```


```{r}
extraversion <- positive_affect + sociability + activity
```

Just to take a look to the data, an histogram of estraversion is
```{r}
hist(extraversion)
```


The third factor of neo_ffi_60 is called openness and is composed by three subscales. The scores on such scales are the following:
```{r}
aesthetic_interests <- 
neo_ffi_60$i13 + abs(neo_ffi_60$i23 - 4) + neo_ffi_60$i43
```


```{r}
intellectual_interests <- 
abs(neo_ffi_60$i48 - 4) + neo_ffi_60$i53 + neo_ffi_60$i58
```


```{r}
unconventionality <- 
abs(neo_ffi_60$i3 - 4) + abs(neo_ffi_60$i8 - 4) + abs(neo_ffi_60$i18 - 4) + abs(neo_ffi_60$i38 - 4)
```


```{r}
openness <- aesthetic_interests + intellectual_interests + unconventionality
```

Just to take a look to the data, an histogram of openness is
```{r}
hist(openness)
```


The fourth factor of neo_ffi_60 is called agreeableness and is composed by two subscales. The scores on such scales are the following:
```{r}
nonantagonistic_orientation <- 
abs(neo_ffi_60$i9 - 4) + abs(neo_ffi_60$i14 - 4) + neo_ffi_60$i19 +  abs(neo_ffi_60$i24 - 4) + abs(neo_ffi_60$i29 - 4) + abs(neo_ffi_60$i44 - 4) + abs(neo_ffi_60$i54 - 4) + abs(neo_ffi_60$i59 - 4)
```


```{r}
prosocial_orientation <- 
neo_ffi_60$i4 + neo_ffi_60$i34 + abs(neo_ffi_60$i39 - 4) + neo_ffi_60$i49
```


```{r}
agreeableness <- nonantagonistic_orientation + prosocial_orientation
```

Just to take a look to the data, an histogram of agreeableness is
```{r}
hist(agreeableness)
```


The fifth factor of neo_ffi_60 is called conscientiousness and is composed by three subscales. The scores on such scales are the following:
```{r}
orderliness <- 
neo_ffi_60$i5 +  neo_ffi_60$i10 + abs(neo_ffi_60$i15 - 4) + abs(neo_ffi_60$i30 - 4) + abs(neo_ffi_60$i55 - 4)
```


```{r}
goal_striving <- 
neo_ffi_60$i25 +  neo_ffi_60$i35 + neo_ffi_60$i60
```


```{r}
dependability <- 
neo_ffi_60$i20 +  neo_ffi_60$i40 + abs(neo_ffi_60$i45 - 4) + neo_ffi_60$i50
```


```{r}
conscientiousness <- orderliness + goal_striving + dependability
```

Just to take a look to the data, an histogram of conscientiousness is
```{r}
hist(conscientiousness)
```

# Scala COPE NVI

Let start with the coding of cope_nvi. First, we select the right columns:
```{r}
cope_nvi <- df %>% 
  select(X76:X135)
```

Then we change the column names to facilitate coding
```{r}
item_names <- paste0("ii", 1:60)
names(cope_nvi) <- item_names
```

Some items are reversed. In that cases, we can compute the right value by using the following formula: abs(x - max).

The first subscale of cope_nvi is called social support. The scores on such scales are the following:
```{r}
social_support <- 
cope_nvi$ii4 + cope_nvi$ii14 + cope_nvi$ii30 + cope_nvi$ii45 + cope_nvi$ii11 + cope_nvi$ii23 + cope_nvi$ii34 + cope_nvi$ii52 + cope_nvi$ii3 + cope_nvi$ii17 + cope_nvi$ii28 + cope_nvi$ii46
```

```{r}
hist(social_support)
```

The second subscale of cope_nvi is called avoiding strategies. The scores on such scale are the following:
```{r}
avoiding_strategies <- 
cope_nvi$ii6 + cope_nvi$ii27 + cope_nvi$ii40 + cope_nvi$ii57 + cope_nvi$ii9 + cope_nvi$ii24 + cope_nvi$ii37 + cope_nvi$ii51 + cope_nvi$ii2 + cope_nvi$ii16 + cope_nvi$ii31 + cope_nvi$ii43 +  cope_nvi$ii12 +  cope_nvi$ii26 +  cope_nvi$ii43 +  cope_nvi$ii35 +  cope_nvi$ii53
```

```{r}
hist(avoiding_strategies)
```

The third subscale of cope_nvi is called positive attitude. The scores on such scale are the following:
```{r}
positive_attitude <- 
cope_nvi$ii10 + cope_nvi$ii22 + cope_nvi$ii41 + cope_nvi$ii49 + cope_nvi$ii1 + cope_nvi$ii29 + cope_nvi$ii38 + cope_nvi$ii59 + cope_nvi$ii13 + cope_nvi$ii21 + cope_nvi$ii44 + cope_nvi$ii54
```

```{r}
hist(positive_attitude)
```

The fourth subscale of cope_nvi is called problem orientation. The scores on such scale are the following:
```{r}
problem_orientation <- 
cope_nvi$ii5 + cope_nvi$ii25 + cope_nvi$ii47 + cope_nvi$ii58 + cope_nvi$ii19 + cope_nvi$ii32 + cope_nvi$ii39 + cope_nvi$ii56 + cope_nvi$ii15 + cope_nvi$ii33 + cope_nvi$ii42 + cope_nvi$ii55
```

```{r}
hist(problem_orientation)
```

The fifth subscale of cope_nvi is called transcendent orientation. The scores on such scale are the following:
```{r}
transcendent_orientation <- 
abs(cope_nvi$ii8 - 5) + abs(cope_nvi$ii20 - 5) + abs(cope_nvi$ii36 - 5) + abs(cope_nvi$ii50 - 5) + cope_nvi$ii7 + cope_nvi$ii18 + cope_nvi$ii48 + cope_nvi$ii60
```

```{r}
hist(transcendent_orientation)
```


# Scala PTGI

Let start with the coding of ptgi. First, we select the right columns:
```{r}
ptgi1 <- df %>% 
  select(X136:X143)
```


```{r}
ptgi2 <- df %>% 
  select(X144:X164)
```

Then we change the column names to facilitate coding
```{r}
item_names <- paste0("it", 1:8)
names(ptgi1) <- item_names
```

COME CODIFICARE LE VARIABILI DI PTGI1??????

```{r}
item_names <- paste0("iii", 1:21)
names(ptgi2) <- item_names
```

```{r}
interpersonal_relationships <-
  ptgi2$iii15 + ptgi2$iii20 + ptgi2$iii9 + ptgi2$iii21 + ptgi2$iii8 + ptgi2$iii16 + ptgi2$iii6
```

```{r}
hist(interpersonal_relationships)
```


```{r}
new_possibilities <-
  ptgi2$iii11 + ptgi2$iii7 + ptgi2$iii3 + ptgi2$iii17 + ptgi2$iii14
```

```{r}
hist(new_possibilities)
```

```{r}
personal_strength <-
  ptgi2$iii10 + ptgi2$iii19 + ptgi2$iii4 + ptgi2$iii12
```

```{r}
hist(personal_strength)
```

```{r}
life_appreciation <-
  ptgi2$iii13 + ptgi2$iii2 + ptgi2$iii1
```

```{r}
hist(life_appreciation)
```


```{r}
spirituality_changes <-
  ptgi2$iii5 + ptgi2$iii18
```

```{r}
hist(spirituality_changes)
```


# Scala IES-R

Let start with the coding of ies_r. First, we select the right columns:
```{r}
ies_r1 <- df %>% 
  select(X165:X170)
```

```{r}
ies_r2 <- df %>% 
  select(X171:X192)
```


Then we change the column names to facilitate coding
```{r}
item_names <- paste0("iit", 1:6)
names(ies_r2) <- item_names
```

COME CODIFICARE QUESTI 6 ITEMS????


```{r}
item_names <- paste0("iiii", 1:22)
names(ies_r2) <- item_names
```


Il massimo punteggio medio di ognuna delle 3 subscale h 4, quindi il punteggio
medio totale massimo della scala IES-R h 12. Bassi punteggi sono migliori. Un
punteggio totale alla IES-R di 33 o superiore su un punteggio massimo di 88
significa la probabile presenza di un PTSD.


```{r}
avoiding <- 
  ies_r2$iiii5 + ies_r2$iiii7 + ies_r2$iiii8 + ies_r2$iiii11 + ies_r2$iiii12 + ies_r2$iiii13 + ies_r2$iiii17 + ies_r2$iiii22
```

```{r}
hist(avoiding)
```

```{r}
intrusivity <- 
  ies_r2$iiii1 + ies_r2$iiii2 + ies_r2$iiii3 + ies_r2$iiii6 + ies_r2$iiii9 + ies_r2$iiii14 + ies_r2$iiii16 + ies_r2$iiii20
```

```{r}
hist(intrusivity)
```

```{r}
iperarousal <-  
  ies_r2$iiii4 + ies_r2$iiii10 + ies_r2$iiii15 + ies_r2$iiii18 + ies_r2$iiii19 + ies_r2$iiii21
```

```{r}
hist(iperarousal)
```

```{r}
ies_r_score <- avoiding + intrusivity + iperarousal
```

```{r}
hist(ies_r_score)
```


I punteggi delle sottoscale del scs sono ottenuti calcolando la media delle risposte nei rispettivi item.
Quindi calcolare la media dei punteggi medi delle sei sottoscale. COME SI FA?


In this approach any mean scale score ranging from 1 to 2.9 could be considered low support; a score of 3 to 5 could be considered moderate support; a score from 5.1 to 7 could be considered high support. This approach would seem to have more
validity, but if you have very few respondents in any of the groups, it could be problematic.


# Scala SCS

Let start with the coding of scs. First, we select the right columns:
```{r}
scs <- df %>% 
  select(X193:X218)
```

Then we change the column names to facilitate coding
```{r}
item_names <- paste0("iiiii", 1:26)
names(scs) <- item_names
```

```{r}
self_kindness <- 
  scs$iiiii5 + scs$iiiii12 + scs$iiiii19 + scs$iiiii23 + scs$iiiii26
```

```{r}
hist(self_kindness)
```

```{r}
self_judgment <- 
  abs(scs$iiiii1 - 6) + abs(scs$iiiii8 - 6) + abs(scs$iiiii11 - 6) + abs(scs$iiiii16 - 6) + abs(scs$iiiii21 - 6)
```

```{r}
hist(self_judgment)
```

```{r}
common_humanity <- 
  scs$iiiii3 + scs$iiiii7 + scs$iiiii10 + scs$iiiii15
```

```{r}
hist(common_humanity)
```

```{r}
isolation <- 
  abs(scs$iiiii4 - 6) + abs(scs$iiiii13 - 6) + abs(scs$iiiii18 - 6) + abs(scs$iiiii25 - 6)
```

```{r}
hist(isolation)
```

```{r}
mindfulness <- 
  scs$iiiii9 + scs$iiiii14 + scs$iiiii17 + scs$iiiii22
```

```{r}
hist(mindfulness)
```

```{r}
over_identification <- 
  abs(scs$iiiii2 - 6) + abs(scs$iiiii6 - 6) + abs(scs$iiiii20 - 6) + abs(scs$iiiii24 - 6)
```

```{r}
hist(over_identification)
```


# Scala MSPSS

Let start with the coding of mspss. First, we select the right columns:
```{r}
mspss <- df %>% 
  select(X219:X230)
```

Then we change the column names to facilitate coding
```{r}
item_names <- paste0("iiiiii", 1:12)
names(mspss) <- item_names
```

```{r}
family <- 
  mspss$iiiiii3 + mspss$iiiiii4 + mspss$iiiiii8 + mspss$iiiiii11
```

```{r}
hist(family)
```

```{r}
friends <- 
  mspss$iiiiii6 + mspss$iiiiii7 + mspss$iiiiii9 + mspss$iiiiii12
```

```{r}
hist(friends)
```

```{r}
significant_other <-
  mspss$iiiiii1 + mspss$iiiiii2 + mspss$iiiiii5 + mspss$iiiiii10
```

```{r}
hist(significant_other)
```



# Replication of path model of Mattson, James, & Engdahl (2018) - Figure 2

Figure 2: 
Adaptive Coping 

```{r}
coping <- social_support + positive_attitude + problem_orientation + transcendent_orientation
ptg <- life_appreciation + new_possibilities + personal_strength + spirituality_changes + interpersonal_relationships

df <- data.frame(openness, coping, ptg)
```

## Multiple imputation

```{r}
temp_data <- mice(df, m=5, maxit=50, meth='pmm', seed=500)
```


```{r}
imp_data <- complete(temp_data, 1)

```

# Mediational analysis (1)

Here, we consider the path analysis model of Mattson, James, & Engdahl (2018) described in their Figure 2.

X: openness
Y: ptg
M: coping

```{r}
imp_data <- imp_data %>% 
  dplyr::rename(
    X = openness,
    Y = ptg,
    M = coping
  )
```


```{r}
model <- ' # direct effect
             Y ~ c*X
           # mediator
             M ~ a*X
             Y ~ b*M
           # indirect effect (a*b)
             ab := a*b
           # total effect
             total := c + (a*b)
         '
```


```{r}
set.seed(1234)
fit1 <- sem(model, data = imp_data)
summary(fit1)
```


# Mediational analysis (2)


```{r}
df2 <- data.frame(extraversion, coping, ptg)
```

X: extraversion
Y: ptg
M: coping

## Multiple imputation

```{r}
temp_data_2 <- mice(df2, m=5, maxit=50, meth='pmm', seed=500)
```


```{r}
imp_data_2 <- complete(temp_data_2, 1)
```

```{r}
imp_data_2 <- imp_data_2 %>% 
  dplyr::rename(
    X = extraversion,
    Y = ptg,
    M = coping
  )
```

```{r}
model2 <- ' # direct effect
             Y ~ c*X
           # mediator
             M ~ a*X
             Y ~ b*M
           # indirect effect (a*b)
             ab := a*b
           # total effect
             total := c + (a*b)
         '
```


```{r}
set.seed(1234)
fit2 <- sem(model2, data = imp_data_2)
summary(fit2)
```


# Replication of path model of Mattson, James, & Engdahl (2018) - Figure 3

```{r}
df <- data.frame(ies_r_score, neuroticism, avoiding_strategies)
```

## Multiple imputation

```{r}
temp_data <- mice(df, m=5, maxit=50, meth='pmm', seed=500)
```


```{r}
imp_data <- complete(temp_data, 1)
```

## Mediational analysis 

Here, we consider the path analysis model of Mattson, James, & Engdahl (2018) described in their Figure 3.

X: neuroticism
Y: ies_r_score
M: avoiding_strategies

```{r}
imp_data <- imp_data %>% 
  dplyr::rename(
    X = neuroticism,
    Y = ies_r_score,
    M = avoiding_strategies
  )
```


```{r}
model <- ' # direct effect
             Y ~ c*X
           # mediator
             M ~ a*X
             Y ~ b*M
           # indirect effect (a*b)
             ab := a*b
           # total effect
             total := c + (a*b)
         '
```


```{r}
set.seed(1234)
fit3 <- sem(model, data = imp_data)
summary(fit3)
```



# Negative Self-compassion as mediating factor 

```{r}
neg_self_compassion <- self_judgment + isolation + over_identification
```


```{r}
df <- data.frame(ies_r_score, neuroticism, neg_self_compassion)
```

## Multiple imputation

```{r}
temp_data <- mice(df, m=5, maxit=50, meth='pmm', seed=500)
```


```{r}
imp_data <- complete(temp_data, 1)
```

## Mediational analysis 

Let us consider the path analysis model of Mattson, James, & Engdahl (2018) described in their Figure 3, but with negative self-compassion instead of maladaptive coping.


```{r}
imp_data <- imp_data %>% 
  dplyr::rename(
    X = neuroticism,
    Y = ies_r_score,
    M = neg_self_compassion
  )
```


```{r}
model <- ' # direct effect
             Y ~ c*X
           # mediator
             M ~ a*X
             Y ~ b*M
           # indirect effect (a*b)
             ab := a*b
           # total effect
             total := c + (a*b)
         '
```


```{r}
set.seed(1234)
fit3 <- sem(model, data = imp_data)
summary(fit3)
```




# Positive Self-compassion as mediating factor 

```{r}
pos_self_compassion <- self_kindness + common_humanity + mindfulness
```


```{r}
df <- data.frame(ptg, extraversion, pos_self_compassion)
```

## Multiple imputation

```{r}
temp_data <- mice(df, m=5, maxit=50, meth='pmm', seed=500)
```


```{r}
imp_data <- complete(temp_data, 1)
```

## Mediational analysis 

Let us consider the path analysis model of Mattson, James, & Engdahl (2018) described in their Figure 2, but with positive self-compassion instead of adaptive coping.


```{r}
imp_data <- imp_data %>% 
  dplyr::rename(
    X = extraversion,
    Y = ptg,
    M = pos_self_compassion
  )
```


```{r}
model <- ' # direct effect
             Y ~ c*X
           # mediator
             M ~ a*X
             Y ~ b*M
           # indirect effect (a*b)
             ab := a*b
           # total effect
             total := c + (a*b)
         '
```


```{r}
set.seed(1234)
fit3 <- sem(model, data = imp_data)
summary(fit3)
```




# Both negative self compassion and avoiding strategies as mediators

```{r}
neg_self_compassion <- self_judgment + isolation + over_identification
df <- data.frame(ies_r_score, neuroticism, avoiding_strategies, neg_self_compassion)
```

## Multiple imputation

```{r}
temp_data <- mice(df, m=5, maxit=50, meth='pmm', seed=500)
```


```{r}
imp_data <- complete(temp_data, 1)
```

## Mediational analysis 

We consider a path analysis model where both negative self-compassion and maladaptive coping are mediating factors

X: neuroticism
Y: ies_r_score
M: avoiding_strategies

```{r}
imp_data <- imp_data %>% 
  dplyr::rename(
    X = neuroticism,
    Y = ies_r_score,
    M1 = avoiding_strategies,
    M2 = neg_self_compassion
  )
```


```{r}
model <- ' # direct effect
             Y ~ c*X
           # mediator
             M1 ~ a*X
             Y ~ b*M1
             M2 ~ d*X
             Y ~ e*M2
           # indirect effect (a*b)
             ab := a*b 
             de := d*e
             abde := a*b + d*e
           # total effect
             total := c + (a*b) + (d*e)
         '
```


```{r}
set.seed(1234)
fit <- sem(model, data = imp_data)
summary(fit)
```














# Positive Self-compassion as causal source and extraversion as the mediating factor 

```{r}
pos_self_compassion <- self_kindness + common_humanity + mindfulness
```


```{r}
df <- data.frame(ptg, extraversion, pos_self_compassion)
```

## Multiple imputation

```{r}
temp_data <- mice(df, m=5, maxit=50, meth='pmm', seed=500)
```


```{r}
imp_data <- complete(temp_data, 1)
```

## Mediational analysis 

Let us consider the path analysis model of Mattson, James, & Engdahl (2018) described in their Figure 2, but with positive self-compassion instead of adaptive coping.


```{r}
imp_data <- imp_data %>% 
  dplyr::rename(
    X = pos_self_compassion ,
    Y = ptg,
    M = extraversion
  )
```


```{r}
model <- ' # direct effect
             Y ~ c*X
           # mediator
             M ~ a*X
             Y ~ b*M
           # indirect effect (a*b)
             ab := a*b
           # total effect
             total := c + (a*b)
         '
```


```{r}
set.seed(1234)
fit3 <- sem(model, data = imp_data)
summary(fit3)
```



```{r}
cor.test(pos_self_compassion, coping, na.rm = TRUE)
```



```{r}
cor.test(neg_self_compassion, avoiding_strategies, na.rm = TRUE)
```

