---
title: "Self-compassion and post-traumatic growth"
author: "[Corrado Caudek](https://ccaudek.github.io/)"
date: "First version 2019-02-14. Last modified `r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    fig_caption: yes
    highlight: pygments
    toc: TRUE
    toc_depth: 2
    number_sections: TRUE
    toc_float:
      smooth_scroll: FALSE
---


```{r}
library("here")
suppressPackageStartupMessages(library("tidyverse"))
suppressPackageStartupMessages(library("lavaan"))
suppressPackageStartupMessages(library("mice"))
library("forcats")
```


```{r}
source(here("libraries", "self_compassion_fnc.R"))
```




```{r}
# To create the data, run:
# source(here("04_import_data.R"))
```


# Read data

```{r}
mydata <- read.csv(
  file=here("data", "rescue_workers.csv"), 
  header=TRUE, 
  sep=";"
)
```


# Replication of the path model of Mattson, James, & Engdahl (2018), fig. 2: Adaptive Coping 


```{r}
## Multiple imputation
# temp_data1 <- mice(df1, m=5, maxit=50, meth='pmm', seed=500, print = FALSE)
# imp_data1 <- complete(temp_data1, 1)
```


## Mediational analysis (1)

```{r}
d <- data.frame(
  x = mydata$openness, 
  m = mydata$cope_nvi, 
  y = mydata$ptg
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```

Only indirect effect through COPE-NVI.


## Mediational analysis (2)

```{r}
d <- data.frame(
  x = mydata$extraversion, 
  m = mydata$cope_nvi, 
  y = mydata$ptg
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```

Both direct effect than indirect effect though COPE-NVI.


## Mediational analysis (3)

```{r}
d <- data.frame(
  x = mydata$neuroticism, 
  m = mydata$cope_nvi, 
  y = mydata$ptg
)
d <- d[complete.cases(d), ]
print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```

Only indirect effect through coping.


## Mediational analysis (4)

```{r}
d <- data.frame(
  x = mydata$agreeableness, 
  m = mydata$cope_nvi, 
  y = mydata$ptg
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```

Only indirect effect through coping.


## Mediational analysis (5)

```{r}
d <- data.frame(
  x = mydata$conscientiousness, 
  m = mydata$cope_nvi, 
  y = mydata$ptg
)
d <- d[complete.cases(d), ]
print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```

Both direct and indirect effects through coping.



## Mediational analysis (6)

Here, we consider the path analysis model of Mattson, James, & Engdahl (2018) 
described in their Figure 3.

X: neuroticism
Y: ies_r_score (assesses subjective distress caused by traumatic events)
M: avoiding_strategies (the second subscale of cope_nvi is called avoiding strategies)

```{r}
d <- data.frame(
  x = mydata$neuroticism, 
  m = mydata$avoiding_strategies,
  y = mydata$ies
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```

Both direct and indirect effects.


## Self-compassion
### Negative Self-compassion as mediating factor 

Let us consider the path analysis model of Mattson, James, & Engdahl (2018) described in their Figure 3, but with negative self-compassion instead of maladaptive coping.

```{r}
d <- data.frame(
  x = mydata$neuroticism, 
  m = mydata$neg_self_compassion,
  y = mydata$ies
)
d <- d[complete.cases(d), ]
print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```




### Positive Self-compassion as mediating factor 

The path analysis model of Mattson, James, & Engdahl (2018) described in their 
Figure 2, but with positive self-compassion instead of adaptive coping.


```{r}
d <- data.frame(
  x = mydata$extraversion, 
  m = mydata$pos_self_compassion,
  y = mydata$ptg
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```



### Positive Self-compassion as mediating factor with Openness

```{r}
d <- data.frame(
  x = mydata$openness, 
  m = mydata$pos_self_compassion,
  y = mydata$ptg
)
d <- d[complete.cases(d), ]
print(cor(d), 3)

m <- mediation_an_1(d)
summary(m)
```


### Negative self-compassion and maladaptive coping as mediators

We consider a path analysis model where both negative self-compassion and 
maladaptive coping are mediating factors:

- X: neuroticism
- Y: ies_r_score
- M1: avoiding_strategies
- M2: neg_self_compassion

```{r}
d <- data.frame(
  y = mydata$ies, 
  m1 = mydata$avoiding_strategies, 
  m2 = mydata$neg_self_compassion,
  x = mydata$neuroticism
)
d <- d[complete.cases(d), ]

print(cor(d), 3)

m <- mediation_an_2(d)
summary(m)
```



### Negative and positive self compassion as mediators

We consider a path analysis model where both negative self-compassion and 
positive self-compassion are mediating factors:


```{r}
d <- data.frame(
  x  = mydata$neuroticism, 
  m1 = mydata$pos_self_compassion, 
  m2 = mydata$neg_self_compassion,
  y  = mydata$ies
)
d <- d[complete.cases(d), ]
print(cor(d), 3)

m <- mediation_an_2(d)
summary(m)
```















<!-- # Self Compassion is the same of coping strategies? -->

<!-- ```{r} -->
<!-- cor.test(pos_self_compassion, coping, na.rm = TRUE) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- plot(pos_self_compassion, coping) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- cor.test(neg_self_compassion, avoiding_strategies, na.rm = TRUE) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- plot(neg_self_compassion, avoiding_strategies) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- self_compassion <- self_judgment + self_kindness + common_humanity + -->
<!--   isolation + over_identification + mindfulness -->
<!-- ``` -->

<!-- ```{r} -->
<!-- summary(self_compassion) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- summary(pos_self_compassion) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- summary(neg_self_compassion) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- summary(avoiding_strategies) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- df$gender <- fct_recode( -->
<!--   df$gender, -->
<!--   "female" = "Femmina", -->
<!--   "male" = "Maschio" -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- df$employment <- fct_recode( -->
<!--   df$employment, -->
<!--   "Dipendente" = "Operaio", -->
<!--   "Dipendente" = "Impiegato", -->
<!--   "Libero professionista" = "Imprenditore", -->
<!--   "Dipendente" = "Dipendente CRI", -->
<!--   "Dipendente" = "Infermiere", -->
<!--   "Dipendente" = "Militare", -->
<!--   "Dipendente" = "Vigile del Fuoco", -->
<!--   "Pensionato" = "pensionato", -->
<!--   "Dipendente" = "Funzionario Pubblico", -->
<!--   "Dipendente" = "Forze dell'Ordine", -->
<!--   "Dipendente" = "Ricercatore", -->
<!--   "Libero professionista" = "Commerciante", -->
<!--   "Dipendente" = "Educatore", -->
<!--   "Dipendente" = "Soccorritore", -->
<!--   "Dipendente" = "Polizia locale", -->
<!--   "Dipendente" = "Polizia Locale", -->
<!--   "Studente" = "Dottoranda", -->
<!--   "Dipendente" = "Medico", -->
<!--   "Pensionato" = "Pensione", -->
<!--   "Dipendente" = "Insegnante" -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- df$is_rescue_worker <- fct_recode( -->
<!--   df$is_rescue_worker, -->
<!--   "Yes" = "Sì", -->
<!--   "Yes" = "Si" -->
<!-- ) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- df <- df %>% -->
<!--   dplyr::rename( -->
<!--     years_experience = `Anni di esperienza TSSA/PTSI (inserire il numero)` -->
<!--   ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- df$last_training <- factor( -->
<!--   df$last_training, -->
<!--   levels = c( -->
<!--     "Più di 1 anno fa", "Meno di 1 anno fa", "Più di 6 mesi fa", "Meno di 6 mesi fa", -->
<!--     "Più di 2 mesi fa", "Meno di 2 mesi fa" -->
<!--   ) -->
<!-- ) -->
<!-- unique(df$last_training) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- df$rate_of_activity <- factor( -->
<!--   df$rate_of_activity, -->
<!--   levels = c( -->
<!--     "1 turno al mese", "Meno di 1 turno al mese", "1 turno ogni due settimane", -->
<!--     "1 turno a settimana", "Più di 1 turno a settimana" -->
<!--   ) -->
<!-- ) -->
<!-- unique(df$rate_of_activity) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- unique(df$job_qualification) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- df$is_job_qualification_invariant <- fct_recode( -->
<!--   df$is_job_qualification_invariant, -->
<!--   "Yes" = "Sì", -->
<!--   "Yes" = "Si" -->
<!-- ) -->
<!-- table(df$is_job_qualification_invariant) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- df$is_team_invariant <- fct_recode( -->
<!--   df$is_team_invariant, -->
<!--   "Yes" = "Sì", -->
<!--   "Yes" = "Si" -->
<!-- ) -->
<!-- table(df$is_team_invariant) -->
<!-- ``` -->


<!-- # Data frame finale -->

<!-- ```{r} -->
<!-- thedat1 <- data.frame( -->
<!--   where = factor(df$where), -->
<!--   id = factor(df$id), -->
<!--   gender = factor(df$gender), -->
<!--   age = df$age, -->
<!--   education = factor(df$education), -->
<!--   employment = factor(df$employment), -->
<!--   is_rescue_worker = factor(df$is_rescue_worker), -->
<!--   red_cross_commeetee_location = factor(df$red_cross_commeetee_location), -->
<!--   rescue_worker_qualification = factor(df$rescue_worker_qualification), -->
<!--   years_experience = factor(df$years_experience), -->
<!--   last_training = factor(df$last_training), -->
<!--   rate_of_activity = factor(df$rate_of_activity), -->
<!--   job_qualification = factor(df$job_qualification), -->
<!--   is_job_qualification_invariant = factor(df$is_job_qualification_invariant), -->
<!--   is_team_invariant = factor(df$is_team_invariant), -->
<!--   neuroticism, -->
<!--   extraversion, -->
<!--   openness, -->
<!--   agreeableness, -->
<!--   conscientiousness, -->
<!--   coping, -->
<!--   ptg, -->
<!--   ies = ies_r_score, -->
<!--   neg_self_compassion, -->
<!--   pos_self_compassion, -->
<!--   family, -->
<!--   friends, -->
<!--   significant_other -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- thedat <- thedat1 %>% -->
<!--   dplyr::filter(is_rescue_worker == "Yes") -->

<!-- # thedat <- thedat2[complete.cases(thedat2), ] -->
<!-- ``` -->

<!-- ```{r} -->
<!-- saveRDS(thedat, file = "rescue_worker.Rds") -->

<!-- write.table( -->
<!--   thedat, -->
<!--   file = "rescue_worker.csv", -->
<!--   sep = ";", -->
<!--   row.names = FALSE -->
<!-- ) -->
<!-- ``` -->


