---
title: "Self-compassion, post-traumatic growth, and PTSD"
author: "[Corrado Caudek](https://ccaudek.github.io/)"
date: "Last modified `r format(Sys.time(), '%Y-%m-%d')`"
fontsize: 11pt
output:
  prettydoc::html_pretty:
    theme: hpstr
    highlight: github
---

```{r, echo=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  strip.white = TRUE
)

suppressPackageStartupMessages(library("here"))
suppressPackageStartupMessages(library("lavaan"))
suppressPackageStartupMessages(library("brms"))
suppressPackageStartupMessages(library("tidyverse"))
library("ggthemes")
suppressPackageStartupMessages(library("viridis"))
library("tidyr")
suppressPackageStartupMessages(library("mice"))
suppressPackageStartupMessages(library("corrplot"))
suppressPackageStartupMessages(library("bayesplot"))
suppressPackageStartupMessages(library("semPlot"))
suppressPackageStartupMessages(library("rio"))
suppressPackageStartupMessages(library("outForest"))
suppressPackageStartupMessages(library("semTools"))
suppressPackageStartupMessages(library("semoutput"))
suppressPackageStartupMessages(library("isotree"))
suppressPackageStartupMessages(library("tidySEM"))
suppressPackageStartupMessages(library("stringr"))
suppressPackageStartupMessages(library("papaja"))

options(max.print = 99999999)

source(here("libraries", "self_compassion_fnc.R"))
```


# Motivation

Self-compassion (SC) has been proposed as a protective factor against PTSD and a factor promoting PTG.

One limit of these studies, however, is that they have often been performed in student populations, that is, in samples in which, supposedly, PTSD and PTG are only present in mild forms, if ever.

Moreover, in recent years, the role of SC has been questioned. For example, Muris, Otgaar and Pfattheicher (2019) maintain that SC is strongly associated with (reversed) Negative Affect and that, once the negative component of SC is removed, the added value of positive SC is marginal.

Furthermore, Geiger, Pfattheicher, Hartung, Weiss, Schindler, and Wilhelm (2018) have  questioned the fact that SC is a construct that does not overlap with Neuroticism. Once Neuroticism is controlled, there is no evidence of a specific contribution of SC.

The purpose of the present study is to evaluate the hypotheses of Muris et al. (2019) and of Geiger et al. (2018) in a sample of rescue workers.


# Prelims 

```{r}
temp <- readRDS(here("data", "processed", "rescue_workers_cleaned_data.rds"))
clean_dat <- temp %>% 
  dplyr::filter(age_imp > 20)
```


```{r, echo=FALSE}
# Save subjects ids
subjects <- data.frame(id = clean_dat$id)
saveRDS(subjects, here("data", "processed", "participants.Rds"))
```


```{r}
psych::describe(clean_dat)
```


Because of kurtosis for a sub-scale of PTG, robust estimation procedure with the Satorra-Bentler corrections were used. 


# Model 0 

M0 considers two endogenous variables: post-traumatic growth (ptgr) and post-traumatic stress (ptss) and their relations with 4 exogenous variables: coping (cope), perceived social support (soc), self-compassion (sc), and neuroticism (neuro). In model M0, only the regression effects of cope and soc are considered. M0 is therefore a baseline model.

I have included the other exogenous variables, also without considering their effects on the endogenous variables, in order to be able to compare different nested models, to test several theoretical questions.


```{r}
model0 <- "

  # post-traumatic growth
  ptgr =~ life_appreciation + new_possibilities + 
          personal_strength + spirituality_changes + 
          interpersonal_relationships
  
  # ptsd
  ptss =~ avoiding + intrusivity + iperarousal
  
  # coping
  cope =~ social_support + avoiding_strategies + 
          positive_attitude + problem_orientation + 
          transcendent_orientation
  
  # perceived social support
  soc =~ family + friends + significant_other
  
  # self-compassion
  sc =~ self_judgment + isolation + over_identification +
        self_kindness + common_humanity + mindfulness
  
  # neuroticism
  neuro =~ negative_affect + self_reproach
  
  # regressions
  ptgr ~ cope + soc  
  ptss ~ cope + soc 

  self_judgment ~~ self_kindness
  "
```



```{r}
fit0 <- lavaan::sem(
  model0,
  data = clean_dat,
  estimator = "MLM",
  std.lv = TRUE
)
```


```{r, echo=FALSE}
fitMeasures(
  fit0, 
  c("chisq", "df", "cfi", "cfi.robust", "nfi", "tli", "tli.robust", 
    "rmsea", "srmr")
)
```


```{r}
lavaan::standardizedSolution(fit0) %>% 
  mutate_if("is.numeric","round",3) %>% 
  filter(op == "=~")
```


# Model 1 

M1 considers, beyond the regression effects of M0, also an effect of self-compassion, but without distinguishing the two components of self-compassion.
Modification indices suggest to add a residual correlation between self_judgment and self_kindness.

```{r}
model1 <- "
  # measurement model
  
  # post-traumatic growth
  ptgr =~ life_appreciation + new_possibilities + 
          personal_strength + spirituality_changes + 
          interpersonal_relationships
  
  # ptsd
  ptss =~ avoiding + intrusivity + iperarousal
  
  # coping
  cope =~ social_support + avoiding_strategies + 
          positive_attitude + problem_orientation + 
          transcendent_orientation
  
  # perceived social support
  soc =~ family + friends + significant_other
  
  # self-compassion
  sc =~ self_judgment + isolation + over_identification +
        self_kindness + common_humanity + mindfulness
  
  # neuroticism
  neuro =~ negative_affect + self_reproach
  
  # regressions
  ptgr ~ cope + soc + sc 
  ptss ~ cope + soc + sc 

  self_judgment ~~ self_kindness
  "
```


```{r}
fit1 <- lavaan::sem(
  model1,
  data = clean_dat,
  estimator = "MLM",
  std.lv = TRUE
)
```

```{r}
anova(fit1, fit0)
```

Model M1 improves the fit respect model M0. But the fit of M1 is still inadequate.


```{r, echo=FALSE}
fitMeasures(
  fit1, 
  c("cfi", "cfi.robust", "tli", "tli.robust", "rmsea", "srmr")
)
```


```{r, eval=FALSE, echo=FALSE}
semPaths(
  fit1, 
  "std",
  edge.label.cex = 0.75, 
  curvePivot = TRUE, 
  title = TRUE,
  fade = FALSE
)
```


# Model 1a 

M1a is an attempt of improving the fit of M1 by considering only a subset of dimensions of coping, because Coping was poorly defined by such indicators.

```{r}
model1a <- "

  # post-traumatic growth
  ptgr =~ life_appreciation + new_possibilities + 
         personal_strength + spirituality_changes + 
         interpersonal_relationships
  
  # ptsd
  ptss =~ avoiding + intrusivity + iperarousal
  
  # coping
  cope =~ positive_attitude + problem_orientation 
   
  # perceived social support
  soc =~ family + friends + significant_other
  
  # self-compassion
  sc =~ self_judgment + isolation + over_identification +
        self_kindness + common_humanity + mindfulness
  
  # neuroticism
  neuro =~ negative_affect + self_reproach
  
  sc ~~ neuro
  soc ~~ cope
  soc ~~ sc
  soc ~~ neuro
  cope ~~ sc
  cope ~~ neuro
  
  # regressions
  ptgr ~ cope + soc + sc 
  ptss ~ cope + soc + sc 
  
  self_judgment ~~ self_kindness
"
```


```{r}
fit1a <- lavaan::sem(
  model1a,
  data = clean_dat,
  estimator = "MLM",
  std.lv = TRUE
)
```


```{r, echo=FALSE}
fitMeasures(
  fit1a, 
  c("cfi", "cfi.robust", "tli", "tli.robust", "rmsea", "srmr")
)
```


```{r}
anova(fit1, fit1a)
```


# Model 2 

M2 distinguishes between the two components of self-compassion.

```{r}
model2 <- "

  # post-traumatic growth
  ptgr =~ life_appreciation + new_possibilities + 
         personal_strength + spirituality_changes + 
         interpersonal_relationships
  
  # ptsd
  ptss =~ avoiding + intrusivity + iperarousal
  
  # coping
  cope =~ positive_attitude + problem_orientation 
   # + transcendent_orientation + avoiding_strategies + social_support 
  
  # perceived social support
  soc =~ family + friends + significant_other
  
  # self-compassion
  nsc =~ self_judgment + isolation + over_identification
  psc =~ self_kindness + common_humanity + mindfulness
  
  # neuroticism
  neuro =~ negative_affect + self_reproach
  
  psc ~~ nsc
  psc ~~ neuro
  nsc ~~ neuro
  soc ~~ cope
  soc ~~ nsc
  soc ~~ psc
  soc ~~ neuro
  cope ~~ nsc
  cope ~~ psc
  cope ~~ neuro
  
  # regressions
  ptgr ~ cope + soc + nsc + psc 
  ptss ~ cope + soc + nsc + psc 

  self_judgment ~~ self_kindness
"
```


```{r}
fit2 <- sem(
  model2,
  data = clean_dat,
  estimator = "MLM",
  std.lv = TRUE
)
```


```{r, echo=FALSE}
fitMeasures(
  fit2, 
  c("cfi", "cfi.robust", "tli", "tli.robust", "rmsea", "srmr")
)
```

The fit improves.

```{r}
anova(fit1a, fit2)
```

```{r}
compareFit(fit2, fit1a, nested = TRUE)
```


# Model 6 

Model M6 adds the regression coefficient for Neuroticism.

```{r}
model6 <- "

  # post-traumatic growth
  ptgr =~ life_appreciation + new_possibilities + 
         personal_strength + spirituality_changes + 
         interpersonal_relationships
         
  # ptsd
  ptss =~ avoiding + intrusivity + iperarousal
  
  # coping
  cope =~ positive_attitude + problem_orientation 

  # perceived social support
  soc =~ family + friends + significant_other
  
  # self-compassion
  psc =~ self_kindness + common_humanity + mindfulness
  nsc =~ self_judgment + isolation + over_identification
  
  # neuroticism
  neuro =~ negative_affect + self_reproach

  # regressions
  ptss ~ cope + soc + nsc + psc + neuro
  ptgr ~ cope + soc + nsc + psc + neuro
  
  # covariances
  self_judgment ~~ self_kindness
"
```


```{r}
fit6 <- sem(
  model6,
  data = clean_dat,
  estimator = "MLM",
  std.lv = TRUE
)
```


```{r}
anova(fit2, fit6)
```

The fit improves and is very good.

```{r, echo=FALSE}
fitMeasures(
  fit6, 
  c("cfi", "cfi.robust", "tli", "tli.robust", "rmsea", "srmr")
)
```

```{r}
summary(
  fit6,
  standardized = TRUE,
  fit.measures = TRUE,
  rsquare = TRUE
)
```



```{r}
semPaths(
  fit6, 
  "std",
  edge.label.cex = 0.75, 
  curvePivot = TRUE, 
  title = TRUE,
  fade = FALSE
)
```



```{r}
lavaan::standardizedSolution(fit6) %>% 
  dplyr::filter(!is.na(pvalue)) %>% 
  arrange(desc(pvalue)) %>% 
  mutate_if("is.numeric","round",3) %>% 
  select(-ci.lower,-ci.upper,-z)

pvalue_cutoff <- 0.05

obj <- semPlot:::semPlotModel(fit6)

# save a copy of the original, so we can compare it later and 
#  be sure we removed only what we intended to remove
original_Pars <- obj@Pars

check_Pars <- obj@Pars %>% 
  dplyr::filter(!(edge %in% c("int","<->") | lhs == rhs)) 
# this is the list of paramater to sift thru

keep_Pars <- obj@Pars %>% 
  dplyr::filter(edge %in% c("int","<->") | lhs == rhs) 
# this is the list of paramater to keep asis

test_against <- lavaan::standardizedSolution(fit6) %>% 
  dplyr::filter(
    pvalue < pvalue_cutoff, rhs != lhs)

test_against_rev <- test_against %>% 
  rename(rhs2 = lhs,
         lhs = rhs) %>% 
  rename(rhs = rhs2)
# for some reason, the rhs and lhs are reversed in the 
# standardizedSolution() output, for some of the values

checked_Pars <-
    check_Pars %>% 
  semi_join(test_against, by = c("lhs", "rhs")) %>% 
  bind_rows(
        check_Pars %>% 
          semi_join(test_against_rev, by = c("lhs", "rhs"))
    )

# I'll have to reverse it myself, and test against both orders
obj@Pars <- keep_Pars %>% 
  bind_rows(checked_Pars)

#let's verify by looking at the list of the edges we removed from the object
anti_join(original_Pars, obj@Pars)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
semPaths(
  obj, 
  "col",
  "std", 
  rotation = 1,
  groups = "latents", 
  pastel = TRUE,
  residuals = FALSE,
  structural = TRUE,
  curvature = 5,
  edge.width = 2,
edge.label.cex = 1.3,
  mar = c(4, 1, 14, 1)
)
```


```{r, eval=FALSE, echo=FALSE}
semPaths(
  fit6, 
  "col",
  "std", 
  rotation = 1,
  groups = "latents", 
  pastel = TRUE,
  residuals = FALSE,
  structural = TRUE,
  curvature = 5,
  edge.width = 2,
  mar = c(3, 1, 12, 1)
)
```

```{r}
standardizedSolution(fit6) %>% 
  dplyr::filter(op == "~" & (lhs == "ptss" | lhs == "ptgr")) %>% 
  select(lhs, rhs, est.std, pvalue)
```


```{r, eval=FALSE, echo=FALSE}
# vlabs <- c(" x1 " = " Vis 1" , " x2 " = " Vis 2" , x3 = " Vis 3" , x4 = " Txt
# 1" , x5 = " Txt 2" , x6 = " Txt 3" , x7 = " Speed 1" , x8 = " Speed 2" ,
# x9 = " Speed 3")
# 
# fit1.t3 <- semTable (
#   fit6, 
#   columns = c(" est " , " se " , "p") , 
#   paramSets = c(" loadings ") , 
#   fits = c(" chisq " , " rmsea ") , 
#   file = file.path ( tempdir , " fit1.t3 ") , 
#   varLabels = vlabs , 
#   longtable = FALSE , 
#   table.float = TRUE , 
#   caption = " Table Floated ( not a longtable )" , 
#   label = "tab : fit1.t3 ")
```


```{r}
graph_sem(model = fit10)
```


# Model 7 

Model 7 remove the two self-compassion regression effects from M6.

```{r}
model7 <- "

  # post-traumatic growth
  ptgr =~ life_appreciation + new_possibilities + 
         personal_strength + spirituality_changes + 
         interpersonal_relationships
         
  # ptss
  ptss =~ avoiding + intrusivity + iperarousal
  
  # coping
  cope =~ positive_attitude + problem_orientation 
  
  # perceived social support
  soc =~ family + friends + significant_other
  
  # neuroticism
  neuro =~ negative_affect + self_reproach
  
  # self-compassion
  nsc =~ self_judgment + isolation + over_identification
  psc =~ self_kindness + common_humanity + mindfulness
  
  # regressions
  ptgr ~ cope + soc + neuro
  ptss ~ cope + soc + neuro
  
# covariances
  self_judgment ~~ self_kindness
"
```


```{r}
fit7 <- sem(
  model7,
  data = clean_dat,
  estimator = "MLM",
  std.lv = TRUE
)
```


```{r}
anova(fit6, fit7)
```

M6 provides a better fit.

```{r, echo=FALSE}
fitMeasures(
  fit7, 
  c("cfi", "cfi.robust", "tli", "tli.robust", "rmsea", "srmr")
)
```


# Model 8 

M8 remove only the regression effect of the negative component of self-compassion from M6.

```{r}
model8 <- "

  # post-traumatic growth
  ptgr =~ life_appreciation + new_possibilities + 
         personal_strength + spirituality_changes + 
         interpersonal_relationships
         
  # ptsd
  ptss =~ avoiding + intrusivity + iperarousal
  
  # coping
  cope =~ positive_attitude + problem_orientation 

  # perceived social support
  soc =~ family + friends + significant_other
  
  # self-compassion
  nsc =~ self_judgment + isolation + over_identification
  psc =~ self_kindness + common_humanity + mindfulness
  
  # neuroticism
  neuro =~ negative_affect + self_reproach

  # regressions
  ptgr ~ cope + soc + psc + neuro
  ptss ~ cope + soc + psc + neuro
  
  # covariances
  self_judgment ~~ self_kindness
"
```

```{r}
fit8 <- sem(
  model8,
  data = clean_dat,
  estimator = "MLM",
  std.lv = TRUE
)
```

The goodness of fit decreases.

```{r}
anova(fit6, fit8)
```


```{r, echo=FALSE}
fitMeasures(
  fit8, 
  c("cfi", "cfi.robust", "tli", "tli.robust", "rmsea", "srmr")
)
```


# Model 9 

M9 removes only the positive component of self-compassion from M6.

```{r}
model9 <- "
  # post-traumatic growth
  ptgr =~ life_appreciation + new_possibilities + 
         personal_strength + spirituality_changes + 
         interpersonal_relationships
         
  # ptsd
  ptss =~ avoiding + intrusivity + iperarousal
  
  # coping
  cope =~ positive_attitude + problem_orientation 

  # perceived social support
  soc =~ family + friends + significant_other
  
  # self-compassion
  nsc =~ self_judgment + isolation + over_identification
  psc =~ self_kindness + common_humanity + mindfulness
  
  # neuroticism
  neuro =~ negative_affect + self_reproach

  # regressions
  ptgr ~ cope + soc + nsc + neuro
  ptss ~ cope + soc + nsc + neuro
  
  # covariances
  self_judgment ~~ self_kindness
"
```


```{r}
fit9 <- sem(
  model9,
  data = clean_dat,
  estimator = "MLM",
  std.lv = TRUE
)
```

The goodness of fit decreases.

```{r}
anova(fit6, fit9)
```


# Model 10

M10: a mediation structure with the two components of self-compassion

```{r}
model10 <- "
  # post-traumatic growth
  ptgr =~ life_appreciation + new_possibilities + 
         personal_strength + spirituality_changes + 
         interpersonal_relationships
         
  # ptsd
  ptss =~ avoiding + intrusivity + iperarousal
  
  # coping
  cope =~ positive_attitude + problem_orientation 

  # perceived social support
  soc =~ family + friends + significant_other
  
  # self-compassion
  nsc =~ self_judgment + isolation + over_identification
  psc =~ self_kindness + common_humanity + mindfulness
  
  # neuroticism
  neuro =~ negative_affect + self_reproach

  # regressions
  ptgr ~ dg_cope*cope + dg_soc*soc + dg_neuro*neuro
  ptss ~ ds_cope*cope + ds_soc*soc + ds_neuro*neuro

  nsc ~ nsc_cope*cope + nsc_soc*soc + nsc_neuro*neuro
  psc ~ psc_cope*cope + psc_soc*soc + psc_neuro*neuro
  
  ptgr ~ ig_nsc*nsc + ig_psc*psc 
  ptss ~ is_nsc*nsc + is_psc*psc
  
  # covariances
  self_judgment ~~ self_kindness
  
  # indirect and total effects
  # cope
  i_cope_s := nsc_cope * is_nsc + psc_cope * is_psc
  i_cope_g := nsc_cope * ig_nsc + psc_cope * ig_psc
  tot_cope_s := i_cope_s + ds_cope
  tot_cope_g := i_cope_g + dg_cope
  tot_cope := i_cope_s + i_cope_g

  # soc
  i_soc_s := nsc_soc * is_nsc + psc_soc * is_psc
  i_soc_g := nsc_soc * ig_nsc + psc_soc * ig_psc
  tot_soc_s := i_soc_s + ds_soc
  tot_soc_g := i_soc_g + dg_soc
  tot_soc := i_soc_s + i_soc_g
  
  # neuro
  i_neuro_s := nsc_neuro * is_nsc + psc_neuro * is_psc
  i_neuro_g := nsc_neuro * ig_nsc + psc_neuro * ig_psc
  tot_neuro_s := i_neuro_s + ds_neuro
  tot_neuro_g := i_neuro_g + dg_neuro
  tot_neuro := i_neuro_s + i_neuro_g
"
```


```{r}
fit10 <- sem(
  model10,
  data = clean_dat,
  estimator = "MLM",
  std.lv = TRUE
)
```

```{r}
fit10_boot <- sem(
  model10,
  data = clean_dat,
  estimator = "ML",
  std.lv = TRUE,
  se = "bootstrap", 
  bootstrap = 10000
)
```



```{r}
parameterestimates(
  fit10_boot, 
  boot.ci.type = "bca.simple", 
  standardized = TRUE) 
```

```{r}
boot_mediation <- parameterEstimates(
  fit10_boot, se = TRUE, zstat = TRUE, pvalue = TRUE, 
                    ci = TRUE, level = 0.95, boot.ci.type = "perc", 
                    standardized = TRUE, remove.system.eq = TRUE,
                    remove.eq = TRUE, remove.ineq = TRUE, remove.def = FALSE, 
                    rsquare = TRUE
  ) %>% 
  dplyr::filter(op == ":=")
boot_mediation
saveRDS(boot_mediation, "boot_mediation.Rds")
```

```{r}
boot_mediation <- readRDS("boot_mediation.Rds")
```

```{r}
foo <- boot_mediation[-c(5, 10, 15), c(1, 5, 6, 9:10)] 

now_names <- c(
   "Ind. eff. coping -> PTSS", 
   "Ind. eff. coping -> PTG", 
   "Tot. eff. coping -> PTSS", 
   "Tot. eff. coping -> PTG", 
   "Ind. eff. soc. supp. -> PTSS",   
   "Ind. eff. soc. supp. -> PTG", 
   "Tot. eff. soc. supp. -> PTSS", 
   "Tot. eff. soc. supp. -> PTG", 
   "Ind. eff. neuro. -> PTSS", 
   "Ind. eff. neuro. -> PTG",  
   "Tot. eff. neuro. -> PTSS", 
   "Tot. eff. neuro. -> PTG"
)

foo$lhs <- now_names

foo %>% 
  knitr::kable(
    col.names = c("Effect", "Estimate", "S.E.", "C.I. lower", "C.I. upper"),
    digits = 3,
    row.names = FALSE
  )
```



```{r}
summary(
  fit10,
  standardized = TRUE,
  fit.measures = TRUE,
  rsquare = TRUE
)
```


```{r}
lavaan::standardizedSolution(fit10) %>% 
  dplyr::filter(!is.na(pvalue)) %>% 
  arrange(desc(pvalue)) %>% 
  mutate_if("is.numeric","round",3) %>% 
  select(-ci.lower,-ci.upper,-z)

pvalue_cutoff <- 0.05

obj <- semPlot:::semPlotModel(fit10)

# save a copy of the original, so we can compare it later and 
#  be sure we removed only what we intended to remove
original_Pars <- obj@Pars

check_Pars <- obj@Pars %>% 
  dplyr::filter(!(edge %in% c("int","<->") | lhs == rhs)) 
# this is the list of paramater to sift thru

keep_Pars <- obj@Pars %>% 
  dplyr::filter(edge %in% c("int","<->") | lhs == rhs) 
# this is the list of paramater to keep asis

test_against <- lavaan::standardizedSolution(fit10) %>% 
  dplyr::filter(
    pvalue < pvalue_cutoff, rhs != lhs)

test_against_rev <- test_against %>% 
  rename(rhs2 = lhs,
         lhs = rhs) %>% 
  rename(rhs = rhs2)
# for some reason, the rhs and lhs are reversed in the 
# standardizedSolution() output, for some of the values

checked_Pars <-
    check_Pars %>% 
  semi_join(test_against, by = c("lhs", "rhs")) %>% 
  bind_rows(
        check_Pars %>% 
          semi_join(test_against_rev, by = c("lhs", "rhs"))
    )

# I'll have to reverse it myself, and test against both orders
obj@Pars <- keep_Pars %>% 
  bind_rows(checked_Pars)

#let's verify by looking at the list of the edges we removed from the object
anti_join(original_Pars, obj@Pars)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
semPaths(
  obj, 
  "col",
  "std", 
  rotation = 1,
  groups = "latents", 
  pastel = TRUE,
  residuals = FALSE,
  structural = TRUE,
  curvature = 5,
  edge.width = 2,
edge.label.cex = 1.3,
  mar = c(4, 1, 14, 1)
)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
semPaths(
  obj, 
  "col",
  "std", 
  rotation = 1,
  groups = "latents", 
  pastel = TRUE,
  residuals = FALSE,
  structural = TRUE,
  curvature = 5,
  edge.width = 2,
  edge.label.cex = 1.3,
  mar = c(4, 1, 14, 1)
)
```

```{r}
std_solution <- lavaan::standardizedSolution(fit10) %>% 
  mutate_if("is.numeric","round",3) %>% 
  filter(op == "~" | op == "~~")
```


```{r}
lay <- get_layout(
  "cope", "soc",  "neuro",
  "nsc", "", "psc",
  "ptss", "", "ptgr", 
  rows = 3)
lay
```

```{r}
graph_sem(fit10, layout = lay)
```

```{r}
graph_data <- prepare_graph(model = fit10, layout = lay)
tidySEM::nodes(graph_data)
```

```{r}
graph_data[[1]]$label[c(2, 7, 9, 10, 12, 14, 15, 24:27)] <- 
  std_solution[c(2, 7, 9, 10, 12, 14, 15, 24:27), 4]
```


```{r}
tidySEM::edges(graph_data)
```

```{r}
tidySEM::nodes(graph_data) <- tidySEM::nodes(graph_data) %>%
  mutate(label = str_to_title(label))
```

```{r}
tidySEM::edges(graph_data) %>%
  mutate(connect_from = replace(connect_from, is.na(curvature), "bottom")) %>%
  mutate(connect_to = replace(connect_to, is.na(curvature), "top")) -> tidySEM::edges(graph_data)
```

```{r}
plot(graph_data)
```

```{r}
graph_sem(model = fit10, layout = lay, angle = 90)
```

```{r}
edges(graph_data)
plot(graph_data)
```

```{r}
chars <- "test"
value <- "es"
str_detect(chars, value)
```


```{r}
lay <- get_layout(
  "", "cope", "soc",  "neuro", "",
  "nsc", "", "", "", "psc",
  "", "ptss", "", "ptgr", "",
  rows = 3)

graph_data <- prepare_graph(model = fit10, layout = lay)
foo <- edges(graph_data) 
foo1 <- foo[c(2, 7, 9:10, 12, 14, 15, 25:27), ]

graph_data$edges <- foo1


plot(graph_data)
```








# Mediation model without distinguishing between positive and negative components of self-compassion.


M10 hypothesizes a mediation structure

```{r}
model11 <- "
  # post-traumatic growth
  ptgr =~ life_appreciation + new_possibilities + 
         personal_strength + spirituality_changes + 
         interpersonal_relationships
         
  # ptsd
  ptss =~ avoiding + intrusivity + iperarousal
  
  # coping
  cope =~ positive_attitude + problem_orientation 

  # perceived social support
  soc =~ family + friends + significant_other
  
  # self-compassion
  sc =~ self_judgment + isolation + over_identification +
        self_kindness + common_humanity + mindfulness
  
  # neuroticism
  neuro =~ negative_affect + self_reproach

  # regressions
  ptgr ~ dg_cope*cope + dg_soc*soc + dg_neuro*neuro
  ptss ~ ds_cope*cope + ds_soc*soc + ds_neuro*neuro

  sc ~ sc_cope*cope + sc_soc*soc + sc_neuro*neuro

  ptgr ~ ig_nsc*sc  
  ptss ~ is_nsc*sc 
  
  # covariances
  self_judgment ~~ self_kindness
"
```


```{r}
fit11 <- sem(
  model11,
  data = clean_dat,
  estimator = "MLM",
  std.lv = TRUE
)
```


```{r}
summary(
  fit11,
  standardized = TRUE,
  fit.measures = TRUE,
  rsquare = TRUE
)
```


```{r}
anova(fit11, fit10)
```

# Mediation model with 2 components of SC and neuroticism as mediators

```{r}
model12 <- "
  # post-traumatic growth
  ptgr =~ life_appreciation + new_possibilities + 
         personal_strength + spirituality_changes + 
         interpersonal_relationships
         
  # ptsd
  ptss =~ avoiding + intrusivity + iperarousal
  
  # coping
  cope =~ positive_attitude + problem_orientation 

  # perceived social support
  soc =~ family + friends + significant_other
  
  # self-compassion
  nsc =~ self_judgment + isolation + over_identification
  psc =~ self_kindness + common_humanity + mindfulness
  
  # neuroticism
  neuro =~ negative_affect + self_reproach

  # regressions
  ptgr ~ dg_cope*cope + dg_soc*soc 
  ptss ~ ds_cope*cope + ds_soc*soc 

  nsc ~ nsc_cope*cope + nsc_soc*soc 
  psc ~ psc_cope*cope + psc_soc*soc 
  neuro ~ n_cope*cope + n_soc*soc
  
  ptgr ~ ig_nsc*nsc + ig_psc*psc + ig_neuro*neuro
  ptss ~ is_nsc*nsc + is_psc*psc + is_neuro*neuro
  
  # covariances
  self_judgment ~~ self_kindness
"
```


```{r}
fit12 <- sem(
  model12,
  data = clean_dat,
  estimator = "MLM",
  std.lv = TRUE,
  optim.dx.tol = TRUE
)
```

```{r}
summary(
  fit12,
  standardized = TRUE,
  fit.measures = TRUE,
  rsquare = TRUE
)
```


```{r}
anova(fit12, fit10)
```

mi <- modindices(fit12)
mi[mi$op == "=~",]







```{r}
d <- clean_dat %>% dplyr::select(where(is.numeric))
R <- cor(d)
```


```{r}

fit10a <- sem(
  model10,
  sample.cov = R,
  sample.nobs = 731,
  std.lv = TRUE
)
```

```{r}
lay <- get_layout(
  "", "cope", "soc",  "neuro", "",
  "nsc", "", "", "", "psc",
  "", "ptss", "", "ptgr", "",
  rows = 3)

graph_data <- prepare_graph(model = fit10a, layout = lay)
plot(graph_data)
```







```{r}
edges(graph_data) %>%
  mutate(colour = "black") %>%
  mutate(colour = replace(colour, from == "visual" & to == "x2", "red")) %>%
  mutate(linetype = 1) %>%
  mutate(linetype = replace(linetype, from == "visual" & to == "x2", 2)) %>%
  mutate(alpha = 1) %>%
  mutate(alpha = replace(alpha, from == "visual" & to == "x2", .5)) -> edges(graph_data)

```

