---
title: "Emergency psychology"
author: "[Corrado Caudek](https://ccaudek.github.io/)"
date: "First version 2019-02-14. Last modified `r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    fig_caption: yes
    highlight: pygments
    toc: TRUE
    toc_depth: 2
    number_sections: TRUE
    toc_float:
      smooth_scroll: FALSE
---

# Set up

```{r setup, include=FALSE}
library("here")
```

## Packages
```{r}
library("googlesheets")
library("tidyverse")
```

Which google sheets do you have access to?
```{r}
gs_ls()
```

Get the google sheet
```{r}
thedat <- gs_title("Sei un soccorritore in Emergenza? (Risposte)")
```

List worksheets
```{r}
gs_ws_ls(thedat)
```

Get data and convert to data.frame
```{r}
dat <- gs_read(ss=thedat, ws = "Risposte del modulo 1", skip=1)
df <- as.data.frame(dat)
```

Rename variables
```{r}
df <- df %>% 
  rename(
    date = `18/01/2019 18.37.49`,
    permission = `Non acconsento`,
    id = AF213019,
    gender = Femmina,
    education = `Laurea magistrale`,
    employment = Operaio,
    is_rescue_worker = Sì,
    red_cross_commeetee_location = grosseto,
    rescue_worker_qualification = Si, 
    years_of_experience = `1`,
    last_training = `Meno di 1 anno fa`,
    rate_of_activity = `1 turno a settimana`,
    job_qualification = Soccorritore,
    is_job_qualification_invariant= Sì_1, 
    work_with_same_team = No,
    age = X231
  ) 
```

The data.frame contains the following scales:

- NEO_FFI_60: 60 items, from X16 to X76
- COPE_NVI: 60 items
- PTGI: 29 items
- IES_R: 28 items
- SCS: 26 items
- MSPSS: 12 items


Let start with the coding of neo_ffi_60. First, we select the right columns:
```{r}
neo_ffi_60 <- df %>% 
  select(X16:X75)
```

Then we change the column names to facilitate coding
```{r}
item_names <- paste0("i", 1:60)
names(neo_ffi_60) <- item_names
```

Some items are reversed. In that cases, we can compute the right value by using the following formula: abs(x - max).

The first subscale of neo_ffi_60 is called negative affect. The scores on such scale are the following:

```{r}
negative_affect <- 
  abs(neo_ffi_60$i1 - 4) + neo_ffi_60$i11 + abs(neo_ffi_60$i16 - 4) + 
  abs(neo_ffi_60$i31 - 4) + abs(neo_ffi_60$i46 - 4)
```

Just to take a look to the data, an histogram of negative affect is
```{r}
hist(negative_affect)
```

```{r}
neuroticism <- negative_affect + self_reproach
```

