---
title: "Emergency psychology"
author: "[Corrado Caudek](https://ccaudek.github.io/)"
date: "First version 2019-02-14. Last modified `r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    fig_caption: yes
    highlight: pygments
    toc: TRUE
    toc_depth: 2
    number_sections: TRUE
    toc_float:
      smooth_scroll: FALSE
---

# Set up

```{r setup, include=FALSE}
library("here")
```

## Packages
```{r}
library("googlesheets")
library("tidyverse")
library("lavaan")
library("mice")
```

Which google sheets do you have access to?
```{r}
# gs_ls()
```

Get the google sheet
```{r}
thedat <- gs_title("Sei un soccorritore in Emergenza? (Lombardia) (Risposte)")
```

List worksheets
```{r}
gs_ws_ls(thedat)
```

Get data and convert to data.frame
```{r}
dat <- gs_read(ss=thedat, ws = "Risposte del modulo 1", skip=1)
df <- as.data.frame(dat)
```

Rename variables
```{r}
df <- df %>% 
  rename(
    date = `Informazioni cronologiche`,
    permission = `Trattamento dei dati personali`,
    id = `Inserisci il codice identificativo come sopra indicato:`,
    gender = Sesso,
    education = `Livello istruzione`,
    employment =  Occupazione,
    is_rescue_worker = `Sei un Soccorritore in Emergenza?`,
    red_cross_commeetee_location =  `Comitato Croce Rossa Italiana di appartenenza (per es. Comitato di Firenze)`,
    rescue_worker_qualification =  `Possiedi la qualifica TSSA/PTSI?`, 
    last_training = `Quando hai effettuato l'ultimo re-training, corso, inerente la qualifica TSSA/FULL-D?`,
    rate_of_activity =  `Con quale frequenza fai turno in Ambulanza?`,
    job_qualification =  `Generalmente quale ruolo ricopri nella squadra?`,
    is_job_qualification_invariant= `Tendi a ricoprire sempre lo stesso ruolo?`,
    is_team_invariant = `Generalmente fai turno sempre con la stessa squadra?`,
    age =  `Quanti anni hai?`
  ) 
```

The data.frame contains the following scales:

- NEO_FFI_60: 60 items, from X17 to X76
- COPE_NVI: 60 items, from X77 to X136
- PTGI: 29 items, X137 to X144, X145 to X165
- IES_R: 28 items, items X166 to X171, X172 to X193
- SCS: 26 items, items X194 to 219
- MSPSS: 12 items, items X220 to 231

```{r}
gender <- df %>% 
  select(gender)
```

```{r}
education <- df %>% 
  select(education)
```

```{r}
employment <- df %>% 
  select(employment)
```

```{r}
is_rescue_worker <- df %>% 
  select(is_rescue_worker)
```

```{r}
red_cross_commeetee_location <- df %>% 
  select(red_cross_commeetee_location)
```

```{r}
rescue_worker_qualification <- df %>% 
  select(rescue_worker_qualification)
```

```{r}
last_training <- df %>% 
  select(last_training)
```

```{r}
rate_of_activity <- df %>% 
  select(rate_of_activity)
```

```{r}
job_qualification <- df %>% 
  select(job_qualification)
```

```{r}
is_job_qualification_invariant <- df %>% 
  select(is_job_qualification_invariant)
```

```{r}
is_team_invariant <- df %>% 
  select(is_team_invariant)
```

```{r}
age <- df %>% 
  select(age)
```


```{r}
str(df)
```


# Scala neo_ffi_60

Let start with the coding of neo_ffi_60. First, we select the right columns:
```{r}
neo_ffi_60 <- df %>% 
  select(X17:X76)
```

Then we change the column names to facilitate coding
```{r}
item_names <- paste0("i", 1:60)
names(neo_ffi_60) <- item_names
```

Some items are reversed. In that cases, we can compute the right value by using the following formula: abs(x - max).

The first factor of neo_ffi_60 is called neutoticism and is composed by two subscales. The scores on such scales are the following:

```{r}
negative_affect <- 
  abs(neo_ffi_60$i1 - 4) + neo_ffi_60$i11 + abs(neo_ffi_60$i16 - 4) + 
  abs(neo_ffi_60$i31 - 4) + abs(neo_ffi_60$i46 - 4)
```



```{r}
self_reproach <-
neo_ffi_60$i6 + neo_ffi_60$i21 + neo_ffi_60$i26 + neo_ffi_60$i36 + neo_ffi_60$i41 + neo_ffi_60$i51 + neo_ffi_60$i56
```

```{r}
neuroticism <- negative_affect + self_reproach
```

Just to take a look to the data, an histogram of neuroticism is
```{r}
hist(neuroticism)
```


The second factor of neo_ffi_60 is called extraversion and is composed by three subscales. The scores on such scales are the following:
```{r}
positive_affect <-
neo_ffi_60$i7 + abs(neo_ffi_60$i12 - 4) + neo_ffi_60$i37
 + abs(neo_ffi_60$i42 - 4)
```


```{r}
sociability <- 
neo_ffi_60$i2 + neo_ffi_60$i17 + abs(neo_ffi_60$i27 - 4) + abs(neo_ffi_60$i57 - 4)
```


```{r}
activity <- 
neo_ffi_60$i22 + neo_ffi_60$i32 + neo_ffi_60$i47 + neo_ffi_60$i52
```


```{r}
extraversion <- positive_affect + sociability + activity
```

Just to take a look to the data, an histogram of estraversion is
```{r}
hist(extraversion)
```


The third factor of neo_ffi_60 is called openness and is composed by three subscales. The scores on such scales are the following:
```{r}
aesthetic_interests <- 
neo_ffi_60$i13 + abs(neo_ffi_60$i23 - 4) + neo_ffi_60$i43
```


```{r}
intellectual_interests <- 
abs(neo_ffi_60$i48 - 4) + neo_ffi_60$i53 + neo_ffi_60$i58
```


```{r}
unconventionality <- 
abs(neo_ffi_60$i3 - 4) + abs(neo_ffi_60$i8 - 4) + abs(neo_ffi_60$i18 - 4) + abs(neo_ffi_60$i38 - 4)
```


```{r}
openness <- aesthetic_interests + intellectual_interests + unconventionality
```

Just to take a look to the data, an histogram of openness is
```{r}
hist(openness)
```


The fourth factor of neo_ffi_60 is called agreeableness and is composed by two subscales. The scores on such scales are the following:
```{r}
nonantagonistic_orientation <- 
abs(neo_ffi_60$i9 - 4) + abs(neo_ffi_60$i14 - 4) + neo_ffi_60$i19 +  abs(neo_ffi_60$i24 - 4) + abs(neo_ffi_60$i29 - 4) + abs(neo_ffi_60$i44 - 4) + abs(neo_ffi_60$i54 - 4) + abs(neo_ffi_60$i59 - 4)
```


```{r}
prosocial_orientation <- 
neo_ffi_60$i4 + neo_ffi_60$i34 + abs(neo_ffi_60$i39 - 4) + neo_ffi_60$i49
```


```{r}
agreeableness <- nonantagonistic_orientation + prosocial_orientation
```

Just to take a look to the data, an histogram of agreeableness is
```{r}
hist(agreeableness)
```


The fifth factor of neo_ffi_60 is called conscientiousness and is composed by three subscales. The scores on such scales are the following:
```{r}
orderliness <- 
neo_ffi_60$i5 +  neo_ffi_60$i10 + abs(neo_ffi_60$i15 - 4) + abs(neo_ffi_60$i30 - 4) + abs(neo_ffi_60$i55 - 4)
```


```{r}
goal_striving <- 
neo_ffi_60$i25 +  neo_ffi_60$i35 + neo_ffi_60$i60
```


```{r}
dependability <- 
neo_ffi_60$i20 +  neo_ffi_60$i40 + abs(neo_ffi_60$i45 - 4) + neo_ffi_60$i50
```


```{r}
conscientiousness <- orderliness + goal_striving + dependability
```

Just to take a look to the data, an histogram of conscientiousness is
```{r}
hist(conscientiousness)
```

# Scala COPE NVI

Let start with the coding of cope_nvi. First, we select the right columns:
```{r}
cope_nvi <- df %>% 
  select(X77:X136)
```

Then we change the column names to facilitate coding
```{r}
item_names <- paste0("ii", 1:60)
names(cope_nvi) <- item_names
```

Some items are reversed. In that cases, we can compute the right value by using the following formula: abs(x - max).

The first subscale of cope_nvi is called social support. The scores on such scales are the following:
```{r}
social_support <- 
cope_nvi$ii4 + cope_nvi$ii14 + cope_nvi$ii30 + cope_nvi$ii45 + cope_nvi$ii11 + cope_nvi$ii23 + cope_nvi$ii34 + cope_nvi$ii52 + cope_nvi$ii3 + cope_nvi$ii17 + cope_nvi$ii28 + cope_nvi$ii46
```

```{r}
hist(social_support)
```

The second subscale of cope_nvi is called avoiding strategies. The scores on such scale are the following:
```{r}
avoiding_strategies <- 
cope_nvi$ii6 + cope_nvi$ii27 + cope_nvi$ii40 + cope_nvi$ii57 + cope_nvi$ii9 + cope_nvi$ii24 + cope_nvi$ii37 + cope_nvi$ii51 + cope_nvi$ii2 + cope_nvi$ii16 + cope_nvi$ii31 + cope_nvi$ii43 +  cope_nvi$ii12 +  cope_nvi$ii26 +  cope_nvi$ii43 +  cope_nvi$ii35 +  cope_nvi$ii53
```

```{r}
hist(avoiding_strategies)
```

The third subscale of cope_nvi is called positive attitude. The scores on such scale are the following:
```{r}
positive_attitude <- 
cope_nvi$ii10 + cope_nvi$ii22 + cope_nvi$ii41 + cope_nvi$ii49 + cope_nvi$ii1 + cope_nvi$ii29 + cope_nvi$ii38 + cope_nvi$ii59 + cope_nvi$ii13 + cope_nvi$ii21 + cope_nvi$ii44 + cope_nvi$ii54
```

```{r}
hist(positive_attitude)
```

The fourth subscale of cope_nvi is called problem orientation. The scores on such scale are the following:
```{r}
problem_orientation <- 
cope_nvi$ii5 + cope_nvi$ii25 + cope_nvi$ii47 + cope_nvi$ii58 + cope_nvi$ii19 + cope_nvi$ii32 + cope_nvi$ii39 + cope_nvi$ii56 + cope_nvi$ii15 + cope_nvi$ii33 + cope_nvi$ii42 + cope_nvi$ii55
```

```{r}
hist(problem_orientation)
```

The fifth subscale of cope_nvi is called transcendent orientation. The scores on such scale are the following:
```{r}
transcendent_orientation <- 
abs(cope_nvi$ii8 - 5) + abs(cope_nvi$ii20 - 5) + abs(cope_nvi$ii36 - 5) + abs(cope_nvi$ii50 - 5) + cope_nvi$ii7 + cope_nvi$ii18 + cope_nvi$ii48 + cope_nvi$ii60
```

```{r}
hist(transcendent_orientation)
```


# Scala PTGI

We rename column and variables of PTG event

```{r}
life_event <- df %>% 
  select(X137)
```
```{r}
time_life_event <- df %>% 
  select(X138)
```
```{r}
rescue_event <- df %>% 
  select(X139)
```
```{r}
time_rescue_event <- df %>% 
  select(X140)
```
```{r}
defusing_ptg <- df %>% 
  select(X141)
```
```{r}
when_defusiong_ptg <- df %>% 
  select(X142)
```
```{r}
debriefing_ptg <- df %>% 
  select(X143)
```
```{r}
when_debriefing_ptg <- df %>% 
  select(X144)
```

Let start with the coding of ptgi. First, we select the right columns:
```{r}
ptgi <- df %>% 
  select(X145:X165)
```

Then we change the column names to facilitate coding

```{r}
item_names <- paste0("iii", 1:21)
names(ptgi) <- item_names
```

```{r}
interpersonal_relationships <-
  ptgi$iii15 + ptgi$iii20 + ptgi$iii9 + ptgi$iii21 + ptgi$iii8 + ptgi$iii16 + ptgi$iii6
```

```{r}
hist(interpersonal_relationships)
```


```{r}
new_possibilities <-
  ptgi$iii11 + ptgi$iii7 + ptgi$iii3 + ptgi$iii17 + ptgi$iii14
```

```{r}
hist(new_possibilities)
```

```{r}
personal_strength <-
  ptgi$iii10 + ptgi$iii19 + ptgi$iii4 + ptgi$iii12
```

```{r}
hist(personal_strength)
```

```{r}
life_appreciation <-
  ptgi$iii13 + ptgi$iii2 + ptgi$iii1
```

```{r}
hist(life_appreciation)
```


```{r}
spirituality_changes <-
  ptgi$iii5 + ptgi$iii18
```

```{r}
hist(spirituality_changes)
```


# Scala IES-R

```{r}
traumatic_event <- df %>% 
  select(X166)
```
```{r}
time_traumatic_event <- df %>% 
  select(X167)
```
```{r}
defusing_ies_r <- df %>% 
  select(X168)
```
```{r}
when_defusing_ies_r <- df %>% 
  select(X169)
```
```{r}
debriefing_ies_r <- df %>% 
  select(X170)
```
```{r}
when_debriefing_ies_r <- df %>% 
  select(X171)
```


Let start with the coding of ies_r. First, we select the right columns:


```{r}
ies_r <- df %>% 
  select(X172:X193)
```


Then we change the column names to facilitate coding


```{r}
item_names <- paste0("iiii", 1:22)
names(ies_r) <- item_names
```


Il massimo punteggio medio di ognuna delle 3 subscale h 4, quindi il punteggio
medio totale massimo della scala IES-R h 12. Bassi punteggi sono migliori. Un
punteggio totale alla IES-R di 33 o superiore su un punteggio massimo di 88
significa la probabile presenza di un PTSD.


```{r}
avoiding <- 
  ies_r$iiii5 + ies_r$iiii7 + ies_r$iiii8 + ies_r$iiii11 + ies_r$iiii12 + ies_r$iiii13 + ies_r$iiii17 + ies_r$iiii22
```

```{r}
hist(avoiding)
```

```{r}
intrusivity <- 
  ies_r$iiii1 + ies_r$iiii2 + ies_r$iiii3 + ies_r$iiii6 + ies_r$iiii9 + ies_r$iiii14 + ies_r$iiii16 + ies_r$iiii20
```

```{r}
hist(intrusivity)
```

```{r}
iperarousal <-  
  ies_r$iiii4 + ies_r$iiii10 + ies_r$iiii15 + ies_r$iiii18 + ies_r$iiii19 + ies_r$iiii21
```

```{r}
hist(iperarousal)
```

```{r}
ies_r_score <- avoiding + intrusivity + iperarousal
```

```{r}
hist(ies_r_score)
```


I punteggi delle sottoscale del scs sono ottenuti calcolando la media delle risposte nei rispettivi item.
Quindi calcolare la media dei punteggi medi delle sei sottoscale. COME SI FA?


In this approach any mean scale score ranging from 1 to 2.9 could be considered low support; a score of 3 to 5 could be considered moderate support; a score from 5.1 to 7 could be considered high support. This approach would seem to have more
validity, but if you have very few respondents in any of the groups, it could be problematic.


# Scala SCS

Let start with the coding of scs. First, we select the right columns:
```{r}
scs <- df %>% 
  select(X194:X219)
```

Then we change the column names to facilitate coding
```{r}
item_names <- paste0("iiiii", 1:26)
names(scs) <- item_names
```

```{r}
self_kindness <- 
  scs$iiiii5 + scs$iiiii12 + scs$iiiii19 + scs$iiiii23 + scs$iiiii26
```

```{r}
hist(self_kindness)
```

```{r}
self_judgment <- 
  abs(scs$iiiii1 - 6) + abs(scs$iiiii8 - 6) + abs(scs$iiiii11 - 6) + abs(scs$iiiii16 - 6) + abs(scs$iiiii21 - 6)
```

```{r}
hist(self_judgment)
```

```{r}
common_humanity <- 
  scs$iiiii3 + scs$iiiii7 + scs$iiiii10 + scs$iiiii15
```

```{r}
hist(common_humanity)
```

```{r}
isolation <- 
  abs(scs$iiiii4 - 6) + abs(scs$iiiii13 - 6) + abs(scs$iiiii18 - 6) + abs(scs$iiiii25 - 6)
```

```{r}
hist(isolation)
```

```{r}
mindfulness <- 
  scs$iiiii9 + scs$iiiii14 + scs$iiiii17 + scs$iiiii22
```

```{r}
hist(mindfulness)
```

```{r}
over_identification <- 
  abs(scs$iiiii2 - 6) + abs(scs$iiiii6 - 6) + abs(scs$iiiii20 - 6) + abs(scs$iiiii24 - 6)
```

```{r}
hist(over_identification)
```


# Scala MSPSS

Let start with the coding of mspss. First, we select the right columns:
```{r}
mspss <- df %>% 
  select(X220:X231)
```

Then we change the column names to facilitate coding
```{r}
item_names <- paste0("iiiiii", 1:12)
names(mspss) <- item_names
```

```{r}
family <- 
  mspss$iiiiii3 + mspss$iiiiii4 + mspss$iiiiii8 + mspss$iiiiii11
```

```{r}
hist(family)
```

```{r}
friends <- 
  mspss$iiiiii6 + mspss$iiiiii7 + mspss$iiiiii9 + mspss$iiiiii12
```

```{r}
hist(friends)
```

```{r}
significant_other <-
  mspss$iiiiii1 + mspss$iiiiii2 + mspss$iiiiii5 + mspss$iiiiii10
```

```{r}
hist(significant_other)
```



# Replication of path model of Mattson, James, & Engdahl (2018) - Figure 2

Figure 2: 
Adaptive Coping 

```{r}
coping <- social_support + positive_attitude + problem_orientation + transcendent_orientation
ptg <- life_appreciation + new_possibilities + personal_strength + spirituality_changes + interpersonal_relationships

df1 <- data.frame(openness, coping, ptg)
```

## Multiple imputation

```{r}
temp_data1 <- mice(df1, m=5, maxit=50, meth='pmm', seed=500)
```


```{r}
imp_data1 <- complete(temp_data1, 1)

```

# Mediational analysis (1)

Here, we consider the path analysis model of Mattson, James, & Engdahl (2018) described in their Figure 2.

X: openness
Y: ptg
M: coping

```{r}
imp_data1 <- imp_data1 %>% 
  dplyr::rename(
    X = openness,
    Y = ptg,
    M = coping
  )
```


```{r}
model <- ' # direct effect
             Y ~ c*X
           # mediator
             M ~ a*X
             Y ~ b*M
           # indirect effect (a*b)
             ab := a*b
           # total effect
             total := c + (a*b)
         '
```


```{r}
set.seed(1234)
fit1 <- sem(model, data = imp_data1)
summary(fit1)
```
```{r}
print ( cor(imp_data1), 3)
```

# Mediational analysis (2)


```{r}
df2 <- data.frame(extraversion, coping, ptg)
```

X: extraversion
Y: ptg
M: coping

## Multiple imputation

```{r}
temp_data2 <- mice(df2, m=5, maxit=50, meth='pmm', seed=500)
```


```{r}
imp_data2 <- complete(temp_data2, 1)
```

```{r}
imp_data2 <- imp_data2 %>% 
  dplyr::rename(
    X = extraversion,
    Y = ptg,
    M = coping
  )
```

```{r}
model2 <- ' # direct effect
             Y ~ c*X
           # mediator
             M ~ a*X
             Y ~ b*M
           # indirect effect (a*b)
             ab := a*b
           # total effect
             total := c + (a*b)
         '
```


```{r}
set.seed(1234)
fit2 <- sem(model2, data = imp_data2)
summary(fit2)
```
```{r}
print ( cor(imp_data2), 3)
```

# Replication of path model of Mattson, James, & Engdahl (2018) - Figure 3

```{r}
df3 <- data.frame(ies_r_score, neuroticism, avoiding_strategies)
```

## Multiple imputation

```{r}
temp_data3 <- mice(df3, m=5, maxit=50, meth='pmm', seed=500)
```


```{r}
imp_data3 <- complete(temp_data3, 1)
```

## Mediational analysis 

Here, we consider the path analysis model of Mattson, James, & Engdahl (2018) described in their Figure 3.

X: neuroticism
Y: ies_r_score
M: avoiding_strategies

```{r}
imp_data3 <- imp_data3 %>% 
  dplyr::rename(
    X = neuroticism,
    Y = ies_r_score,
    M = avoiding_strategies
  )
```


```{r}
model <- ' # direct effect
             Y ~ c*X
           # mediator
             M ~ a*X
             Y ~ b*M
           # indirect effect (a*b)
             ab := a*b
           # total effect
             total := c + (a*b)
         '
```


```{r}
set.seed(1234)
fit3 <- sem(model, data = imp_data3)
summary(fit3)
```
```{r}
print ( cor(imp_data3), 3)
```


# Negative Self-compassion as mediating factor 

```{r}
neg_self_compassion <- self_judgment + isolation + over_identification
```


```{r}
df4 <- data.frame(ies_r_score, neuroticism, neg_self_compassion)
```

## Multiple imputation

```{r}
temp_data4 <- mice(df4, m=5, maxit=50, meth='pmm', seed=500)
```


```{r}
imp_data4 <- complete(temp_data4, 1)
```

## Mediational analysis 

Let us consider the path analysis model of Mattson, James, & Engdahl (2018) described in their Figure 3, but with negative self-compassion instead of maladaptive coping.


```{r}
imp_data4 <- imp_data4 %>% 
  dplyr::rename(
    X = neuroticism,
    Y = ies_r_score,
    M = neg_self_compassion
  )
```


```{r}
model <- ' # direct effect
             Y ~ c*X
           # mediator
             M ~ a*X
             Y ~ b*M
           # indirect effect (a*b)
             ab := a*b
           # total effect
             total := c + (a*b)
         '
```


```{r}
set.seed(1234)
fit4 <- sem(model, data = imp_data4)
summary(fit4)
```

```{r}
print ( cor(imp_data4), 3)
```


# Positive Self-compassion as mediating factor 

```{r}
pos_self_compassion <- self_kindness + common_humanity + mindfulness
```


```{r}
df5 <- data.frame(ptg, extraversion, pos_self_compassion)
```

## Multiple imputation

```{r}
temp_data5 <- mice(df5, m=5, maxit=50, meth='pmm', seed=500)
```


```{r}
imp_data5 <- complete(temp_data5, 1)
```

## Mediational analysis 

Let us consider the path analysis model of Mattson, James, & Engdahl (2018) described in their Figure 2, but with positive self-compassion instead of adaptive coping.


```{r}
imp_data5 <- imp_data5 %>% 
  dplyr::rename(
    X = extraversion,
    Y = ptg,
    M = pos_self_compassion
  )
```


```{r}
model <- ' # direct effect
             Y ~ c*X
           # mediator
             M ~ a*X
             Y ~ b*M
           # indirect effect (a*b)
             ab := a*b
           # total effect
             total := c + (a*b)
         '
```


```{r}
set.seed(1234)
fit5 <- sem(model, data = imp_data5)
summary(fit5)
```
```{r}
print ( cor(imp_data5), 3)
```



# Positive Self-compassion as mediating factor with Openness

```{r}
pos_self_compassion <- self_kindness + common_humanity + mindfulness
```


```{r}
df6 <- data.frame(ptg, openness, pos_self_compassion)
```

## Multiple imputation

```{r}
temp_data6 <- mice(df6, m=5, maxit=50, meth='pmm', seed=500)
```


```{r}
imp_data6 <- complete(temp_data6, 1)
```

## Mediational analysis 

Let us consider the path analysis model of Mattson, James, & Engdahl (2018) described in their Figure 2, but with positive self-compassion instead of adaptive coping.


```{r}
imp_data6 <- imp_data6 %>% 
  dplyr::rename(
    X = openness,
    Y = ptg,
    M = pos_self_compassion
  )
```


```{r}
model <- ' # direct effect
             Y ~ c*X
           # mediator
             M ~ a*X
             Y ~ b*M
           # indirect effect (a*b)
             ab := a*b
           # total effect
             total := c + (a*b)
         '
```


```{r}
set.seed(1234)
fit6 <- sem(model, data = imp_data6)
summary(fit6)
```
```{r}
print ( cor(imp_data6), 3)
```

# Both negative self compassion and avoiding strategies as mediators

```{r}
neg_self_compassion <- self_judgment + isolation + over_identification
df7 <- data.frame(ies_r_score, neuroticism, avoiding_strategies, neg_self_compassion)
```

## Multiple imputation

```{r}
temp_data7 <- mice(df7, m=5, maxit=50, meth='pmm', seed=500)
```


```{r}
imp_data7 <- complete(temp_data7, 1)
```

## Mediational analysis 

We consider a path analysis model where both negative self-compassion and maladaptive coping are mediating factors

X: neuroticism
Y: ies_r_score
M1: avoiding_strategies
M2: neg_self_compassion

```{r}
imp_data7 <- imp_data7 %>% 
  dplyr::rename(
    X = neuroticism,
    Y = ies_r_score,
    M1 = avoiding_strategies,
    M2 = neg_self_compassion
  )
```


```{r}
model <- ' # direct effect
             Y ~ c*X
           # mediator
             M1 ~ a*X
             Y ~ b*M1
             M2 ~ d*X
             Y ~ e*M2
           # indirect effect (a*b)
             ab := a*b 
             de := d*e
             abde := a*b + d*e
           # total effect
             total := c + (a*b) + (d*e)
         '
```


```{r}
set.seed(1234)
fit7 <- sem(model, data = imp_data7)
summary(fit7)
```
```{r}
print ( cor(imp_data7), 3)
```


# Self Compassion is the same of coping strategies?

```{r}
cor.test(pos_self_compassion, coping, na.rm = TRUE)
```

```{r}
plot(pos_self_compassion, coping)
```


```{r}
cor.test(neg_self_compassion, avoiding_strategies, na.rm = TRUE)
```

```{r}
plot(neg_self_compassion, avoiding_strategies)
```

```{r}
self_compassion <- self_judgment + self_kindness + common_humanity + isolation + over_identification + mindfulness
```

```{r}
summary(self_compassion)
```
```{r}
summary(pos_self_compassion)
```
```{r}
summary(neg_self_compassion)
```

```{r}
summary(avoiding_strategies)
```

