---
title: "Emergency psychology -- Toscana and Lombardia"
author: "[Corrado Caudek](https://ccaudek.github.io/)"
date: "First version 2019-02-14. Last modified `r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    fig_caption: yes
    highlight: pygments
    toc: TRUE
    toc_depth: 2
    number_sections: TRUE
    toc_float:
      smooth_scroll: FALSE
---

- neo_ffi_60: 
neuroticism extraversion openness agreeableness conscientiousness

- COPE:
social_support avoiding_strategies positive_attitude problem_orientation transcendent_orientation 
coping <- social_support + positive_attitude + problem_orientation + transcendent_orientation

- PTG:
interpersonal_relationships new_possibilities personal_strength life_appreciation spirituality_changes 
ptg <- life_appreciation + new_possibilities + personal_strength + spirituality_changes + interpersonal_relationships

- IES-R:
avoiding intrusivity iperarousal (components of PTSD)
ies_r_score <- avoiding + intrusivity + iperarousal

- SCS:
self_kindness self_judgment common_humanity isolation mindfulness over_identification
neg_self_compassion <- self_judgment + isolation + over_identification
pos_self_compassion <- self_kindness + common_humanity + mindfulness

- MSPSS:
family friends significant_other 



# Set up

```{r setup, include=FALSE}
library("here")
```

## Packages
```{r}
suppressPackageStartupMessages(library("googlesheets")) 
suppressPackageStartupMessages(library("tidyverse"))
suppressPackageStartupMessages(library("lavaan"))
suppressPackageStartupMessages(library("mice"))
library("forcats")
```


# Get the google sheet for Toscana

```{r}
thedat <- gs_title("Sei un soccorritore in Emergenza? (Risposte)")
```

List worksheets
```{r}
gs_ws_ls(thedat)
```

Get data and convert to data.frame
```{r}
dat <- gs_read(ss=thedat, ws = "Risposte del modulo 1", skip=1)
df_toscana <- as.data.frame(dat)
df_toscana$where <- "toscana"
```


# Get the google sheet for Lombardia
```{r}
thedat <- gs_title("Sei un soccorritore in Emergenza? (Lombardia) (Risposte)")
```

List worksheets
```{r}
gs_ws_ls(thedat)
```

Get data and convert to data.frame
```{r}
dat <- gs_read(ss=thedat, ws = "Risposte del modulo 1", skip=1)
df_lombardia <- as.data.frame(dat)
df_lombardia$where <- "lombardia"
```

## Combine the two data.frames

```{r}
df <- rbind(df_toscana, df_lombardia)
```


## Rename variables
```{r}
df <- df %>% 
  rename(
    date = `Informazioni cronologiche`,
    permission = `Trattamento dei dati personali`,
    id = `Inserisci il codice identificativo come sopra indicato:`,
    gender = Sesso,
    education = `Livello istruzione`,
    employment =  Occupazione,
    is_rescue_worker = `Sei un Soccorritore in Emergenza?`,
    red_cross_commeetee_location =  `Comitato Croce Rossa Italiana di appartenenza (per es. Comitato di Firenze)`,
    rescue_worker_qualification =  `Possiedi la qualifica TSSA/PTSI?`, 
    last_training = `Quando hai effettuato l'ultimo re-training, corso, inerente la qualifica TSSA/FULL-D?`,
    rate_of_activity =  `Con quale frequenza fai turno in Ambulanza?`,
    job_qualification =  `Generalmente quale ruolo ricopri nella squadra?`,
    is_job_qualification_invariant= `Tendi a ricoprire sempre lo stesso ruolo?`,
    is_team_invariant = `Generalmente fai turno sempre con la stessa squadra?`,
    age =  `Quanti anni hai?`
  ) 
```

The data.frame contains the following scales:

- NEO_FFI_60: 60 items, from X17 to X76
- COPE_NVI: 60 items, from X77 to X136
- PTGI: 29 items, X137 to X144, X145 to X165
- IES_R: 28 items, items X166 to X171, X172 to X193
- SCS: 26 items, items X194 to 219
- MSPSS: 12 items, items X220 to 231

```{r}
gender <- df %>% 
  select(gender)
```

```{r}
education <- df %>% 
  select(education)
```

```{r}
employment <- df %>% 
  select(employment)
```

```{r}
is_rescue_worker <- df %>% 
  select(is_rescue_worker)
```

```{r}
red_cross_commeetee_location <- df %>% 
  select(red_cross_commeetee_location)
```

```{r}
rescue_worker_qualification <- df %>% 
  select(rescue_worker_qualification)
```

```{r}
last_training <- df %>% 
  select(last_training)
```

```{r}
rate_of_activity <- df %>% 
  select(rate_of_activity)
```

```{r}
job_qualification <- df %>% 
  select(job_qualification)
```

```{r}
is_job_qualification_invariant <- df %>% 
  select(is_job_qualification_invariant)
```

```{r}
is_team_invariant <- df %>% 
  select(is_team_invariant)
```

```{r}
age <- df %>% 
  select(age)
```

```{r}
str(df)
```


# NEO-FIve Factor Inventory (NEO-FFI)

NEO-FFI measures five core personality traits: neuroticism, openness, agreeableness, and conscientiousness.

First, let's select the right columns:
```{r}
neo_ffi_60 <- df %>% 
  select(X17:X76)
```

Then we change the column names to facilitate coding
```{r}
item_names <- paste0("i", 1:60)
names(neo_ffi_60) <- item_names
```

Some items are reversed. In that cases, we can compute the right value by using the following formula: abs(x - max).

## Neuroticism

The first factor of neo_ffi_60 is called *neuroticism* and is composed by two subscales. The scores on such scales are the following:

Negative affect:
```{r}
negative_affect <- 
  abs(neo_ffi_60$i1 - 4) + neo_ffi_60$i11 + abs(neo_ffi_60$i16 - 4) + 
  abs(neo_ffi_60$i31 - 4) + abs(neo_ffi_60$i46 - 4)
```

Self reproach:
```{r}
self_reproach <-
neo_ffi_60$i6 + neo_ffi_60$i21 + neo_ffi_60$i26 + neo_ffi_60$i36 + neo_ffi_60$i41 + neo_ffi_60$i51 + neo_ffi_60$i56
```

```{r}
neuroticism <- negative_affect + self_reproach
```

Just to take a look to the data, an histogram of neuroticism is
```{r}
hist(neuroticism)
```

## Extroversion

The second factor of neo_ffi_60 is called *extraversion* and is composed by three subscales. The scores on such scales are the following:
```{r}
positive_affect <- 
  neo_ffi_60$i7 + abs(neo_ffi_60$i12 - 4) + neo_ffi_60$i37 + abs(neo_ffi_60$i42 - 4)
```


```{r}
sociability <- 
  neo_ffi_60$i2 + neo_ffi_60$i17 + abs(neo_ffi_60$i27 - 4) + abs(neo_ffi_60$i57 - 4)
```

```{r}
activity <- 
  neo_ffi_60$i22 + neo_ffi_60$i32 + neo_ffi_60$i47 + neo_ffi_60$i52
```

```{r}
extraversion <- 
  positive_affect + sociability + activity
```

Just to take a look to the data, an histogram of estraversion is
```{r}
hist(extraversion)
```

## Onenness

The third factor of neo_ffi_60 is called *openness* and is composed by three subscales. 
The scores on such scales are the following.

Aesthetic interests:
```{r}
aesthetic_interests <- 
  neo_ffi_60$i13 + abs(neo_ffi_60$i23 - 4) + neo_ffi_60$i43
```

Intellectual interests:
```{r}
intellectual_interests <- 
  abs(neo_ffi_60$i48 - 4) + neo_ffi_60$i53 + neo_ffi_60$i58
```

Unconventionality:
```{r}
unconventionality <- 
  abs(neo_ffi_60$i3 - 4) + abs(neo_ffi_60$i8 - 4) + abs(neo_ffi_60$i18 - 4) + abs(neo_ffi_60$i38 - 4)
```

```{r}
openness <- aesthetic_interests + intellectual_interests + unconventionality
```

Just to take a look to the data, an histogram of openness is
```{r}
hist(openness)
```

## Agreeableness

The fourth factor of neo_ffi_60 is called *agreeableness* and is composed by two subscales. 
The scores on such scales are the following.

Nonantagonistic orientation:
```{r}
nonantagonistic_orientation <- 
abs(neo_ffi_60$i9 - 4) + abs(neo_ffi_60$i14 - 4) + neo_ffi_60$i19 +  abs(neo_ffi_60$i24 - 4) + abs(neo_ffi_60$i29 - 4) + abs(neo_ffi_60$i44 - 4) + abs(neo_ffi_60$i54 - 4) + abs(neo_ffi_60$i59 - 4)
```

Prosocial orientation:
```{r}
prosocial_orientation <- 
neo_ffi_60$i4 + neo_ffi_60$i34 + abs(neo_ffi_60$i39 - 4) + neo_ffi_60$i49
```


```{r}
agreeableness <- nonantagonistic_orientation + prosocial_orientation
```

Just to take a look to the data, an histogram of agreeableness is
```{r}
hist(agreeableness)
```

## Conscientiousness

The fifth factor of neo_ffi_60 is called *conscientiousness* and is composed by three subscales. 
The scores on such scales are the following.

Orderliness:
```{r}
orderliness <- 
neo_ffi_60$i5 +  neo_ffi_60$i10 + abs(neo_ffi_60$i15 - 4) + abs(neo_ffi_60$i30 - 4) + abs(neo_ffi_60$i55 - 4)
```

Goal striving:
```{r}
goal_striving <- 
neo_ffi_60$i25 +  neo_ffi_60$i35 + neo_ffi_60$i60
```

Dependability:
```{r}
dependability <- 
neo_ffi_60$i20 +  neo_ffi_60$i40 + abs(neo_ffi_60$i45 - 4) + neo_ffi_60$i50
```

```{r}
conscientiousness <- orderliness + goal_striving + dependability
```

Just to take a look to the data, an histogram of conscientiousness is
```{r}
hist(conscientiousness)
```


# Coping Orientation to Problems Experienced (COPE-NVI) 

COPE-NVI was devised to measure coping strategies on five levels: 

- problem-oriented coping strategies, 
- avoidance strategies, 
- social-support strategies,
- positive attitude,
- transcendent orientation.

Let start with the coding of cope_nvi. 
First, we select the right columns:
```{r}
cope_nvi <- df %>% 
  select(X77:X136)
```

Then we change the column names to facilitate coding
```{r}
item_names <- paste0("ii", 1:60)
names(cope_nvi) <- item_names
```

Some items are reversed. In that cases, we can compute the right value by using the following formula: abs(x - max).

## Social support

The first subscale of cope_nvi is called *social support*. The scores on such scales are the following:
```{r}
social_support <- 
  cope_nvi$ii4 + cope_nvi$ii14 + cope_nvi$ii30 + cope_nvi$ii45 + cope_nvi$ii11 + 
  cope_nvi$ii23 + cope_nvi$ii34 + cope_nvi$ii52 + cope_nvi$ii3 + cope_nvi$ii17 + 
  cope_nvi$ii28 + cope_nvi$ii46
```

```{r}
hist(social_support)
```

## Avoiding strategies

The second subscale of cope_nvi is called avoiding strategies. 
The scores on such scale are the following:

```{r}
avoiding_strategies <- 
  cope_nvi$ii6 + cope_nvi$ii27 + cope_nvi$ii40 + cope_nvi$ii57 + cope_nvi$ii9 + 
  cope_nvi$ii24 + cope_nvi$ii37 + cope_nvi$ii51 + cope_nvi$ii2 + cope_nvi$ii16 + 
  cope_nvi$ii31 + cope_nvi$ii43 +  cope_nvi$ii12 +  cope_nvi$ii26 + cope_nvi$ii43 +
  cope_nvi$ii35 + cope_nvi$ii53
```

```{r}
hist(avoiding_strategies)
```

## Positive attitude

The third subscale of cope_nvi is called positive attitude. 
The scores on such scale are the following:

```{r}
positive_attitude <- cope_nvi$ii10 + cope_nvi$ii22 + cope_nvi$ii41 + 
  cope_nvi$ii49 + cope_nvi$ii1 + cope_nvi$ii29 + cope_nvi$ii38 + cope_nvi$ii59 + 
  cope_nvi$ii13 + cope_nvi$ii21 + cope_nvi$ii44 + cope_nvi$ii54
```

```{r}
hist(positive_attitude)
```

## Problem orientation

The fourth subscale of cope_nvi is called problem orientation. 
The scores on such scale are the following:

```{r}
problem_orientation <- cope_nvi$ii5 + cope_nvi$ii25 + cope_nvi$ii47 + 
  cope_nvi$ii58 + cope_nvi$ii19 + cope_nvi$ii32 + cope_nvi$ii39 + 
  cope_nvi$ii56 + cope_nvi$ii15 + cope_nvi$ii33 + cope_nvi$ii42 + 
  cope_nvi$ii55
```

```{r}
hist(problem_orientation)
```

## Transcendent orientation

The fifth subscale of cope_nvi is called transcendent orientation. 
The scores on such scale are the following:

```{r}
transcendent_orientation <- abs(cope_nvi$ii8 - 5) + abs(cope_nvi$ii20 - 5) + 
  abs(cope_nvi$ii36 - 5) + abs(cope_nvi$ii50 - 5) + cope_nvi$ii7 + 
  cope_nvi$ii18 + cope_nvi$ii48 + cope_nvi$ii60
```

```{r}
hist(transcendent_orientation)
```


# Post Traumatic Growth Inventory (PTGI)

PTGI is an instrument for assessing positive outcomes reported by persons who have experienced traumatic events.

We rename column and variables of PTG event

```{r}
life_event <- df %>% 
  select(X137)
```
```{r}
time_life_event <- df %>% 
  select(X138)
```
```{r}
rescue_event <- df %>% 
  select(X139)
```
```{r}
time_rescue_event <- df %>% 
  select(X140)
```
```{r}
defusing_ptg <- df %>% 
  select(X141)
```
```{r}
when_defusiong_ptg <- df %>% 
  select(X142)
```
```{r}
debriefing_ptg <- df %>% 
  select(X143)
```
```{r}
when_debriefing_ptg <- df %>% 
  select(X144)
```

Let start with the coding of ptgi. First, we select the right columns:
```{r}
ptgi <- df %>% 
  select(X145:X165)
```

Then we change the column names to facilitate coding

```{r}
item_names <- paste0("iii", 1:21)
names(ptgi) <- item_names
```

## Relating to Others
```{r}
interpersonal_relationships <-
  ptgi$iii15 + ptgi$iii20 + ptgi$iii9 + ptgi$iii21 + ptgi$iii8 + ptgi$iii16 + ptgi$iii6
```

```{r}
hist(interpersonal_relationships)
```

## New Possibilities
```{r}
new_possibilities <-
  ptgi$iii11 + ptgi$iii7 + ptgi$iii3 + ptgi$iii17 + ptgi$iii14
```

```{r}
hist(new_possibilities)
```

## Personal Strength
```{r}
personal_strength <-
  ptgi$iii10 + ptgi$iii19 + ptgi$iii4 + ptgi$iii12
```

```{r}
hist(personal_strength)
```

## Appreciation
```{r}
life_appreciation <-
  ptgi$iii13 + ptgi$iii2 + ptgi$iii1
```

```{r}
hist(life_appreciation)
```

## Spiritual Enhancement
```{r}
spirituality_changes <-
  ptgi$iii5 + ptgi$iii18
```

```{r}
hist(spirituality_changes)
```



# Impact of Event Scale - Revised (IES-R)

The IES-R is a 22-item self-report measure (for DSM-IV) that assesses subjective distress caused by traumatic events.
The IES-R yields a total score (ranging from 0 to 88) and subscale scores can also be calculated for the Intrusion, Avoidance, and Hyperarousal subscales.
Il massimo punteggio medio di ognuna delle 3 subscale è 4, quindi il punteggio medio totale massimo della scala IES-R è 12. 
Bassi punteggi sono migliori. 
Un punteggio totale alla IES-R di 33 o superiore su un punteggio massimo di 88 significa la probabile presenza di un PTSD.


```{r}
traumatic_event <- df %>% 
  select(X166)
```
```{r}
time_traumatic_event <- df %>% 
  select(X167)
```
```{r}
defusing_ies_r <- df %>% 
  select(X168)
```
```{r}
when_defusing_ies_r <- df %>% 
  select(X169)
```
```{r}
debriefing_ies_r <- df %>% 
  select(X170)
```
```{r}
when_debriefing_ies_r <- df %>% 
  select(X171)
```


Let start with the coding of ies_r. 
First, we select the right columns:
```{r}
ies_r <- df %>% 
  select(X172:X193)
```

Then we change the column names to facilitate coding
```{r}
item_names <- paste0("iiii", 1:22)
names(ies_r) <- item_names
```

## Avoidance
```{r}
avoiding <- 
  ies_r$iiii5 + ies_r$iiii7 + ies_r$iiii8 + ies_r$iiii11 + ies_r$iiii12 + 
  ies_r$iiii13 + ies_r$iiii17 + ies_r$iiii22
```

```{r}
hist(avoiding)
```

## Intrusion
```{r}
intrusivity <- 
  ies_r$iiii1 + ies_r$iiii2 + ies_r$iiii3 + ies_r$iiii6 + ies_r$iiii9 + 
  ies_r$iiii14 + ies_r$iiii16 + ies_r$iiii20
```

```{r}
hist(intrusivity)
```

## Hyperarousal

```{r}
iperarousal <-  
  ies_r$iiii4 + ies_r$iiii10 + ies_r$iiii15 + ies_r$iiii18 + ies_r$iiii19 + ies_r$iiii21
```

```{r}
hist(iperarousal)
```

Total score
```{r}
ies_r_score <- avoiding + intrusivity + iperarousal
```

```{r}
hist(ies_r_score)
```



# Self-Compassion Scale (SCS)

The Self-Compassion Scale (SCS) is used to assess how people treated themselves in difficult times (Neff 2003a). 
It includes 26 items across six subscales: 

- Self-Kindness, 
- Self-Judgment, 
- Common Humanity, 
- Isolation, 
- Mindfulness, 
- Overidentification

I punteggi delle sottoscale del scs sono ottenuti calcolando la media delle risposte nei rispettivi item.
Quindi calcolare la media dei punteggi medi delle sei sottoscale. COME SI FA?

In this approach any mean scale score ranging from 1 to 2.9 could be considered low support; a score of 3 to 5 could be considered moderate support; a score from 5.1 to 7 could be considered high support. 
This approach would seem to have more validity, but if you have very few respondents in any of the groups, it could be problematic.


Let start with the coding of scs. First, we select the right columns:
```{r}
scs <- df %>% 
  select(X194:X219)
```

Then we change the column names to facilitate coding
```{r}
item_names <- paste0("iiiii", 1:26)
names(scs) <- item_names
```

## Self-Kindness

```{r}
self_kindness <- 
  scs$iiiii5 + scs$iiiii12 + scs$iiiii19 + scs$iiiii23 + scs$iiiii26
```

```{r}
hist(self_kindness)
```


## Self-Judgment

```{r}
self_judgment <- 
  abs(scs$iiiii1 - 6) + abs(scs$iiiii8 - 6) + abs(scs$iiiii11 - 6) + abs(scs$iiiii16 - 6) + abs(scs$iiiii21 - 6)
```

```{r}
hist(self_judgment)
```


## Common Humanity

```{r}
common_humanity <- 
  scs$iiiii3 + scs$iiiii7 + scs$iiiii10 + scs$iiiii15
```

```{r}
hist(common_humanity)
```


## Isolation

```{r}
isolation <- 
  abs(scs$iiiii4 - 6) + abs(scs$iiiii13 - 6) + abs(scs$iiiii18 - 6) + abs(scs$iiiii25 - 6)
```

```{r}
hist(isolation)
```

## Mindfulness

```{r}
mindfulness <- 
  scs$iiiii9 + scs$iiiii14 + scs$iiiii17 + scs$iiiii22
```

```{r}
hist(mindfulness)
```


## Overidentification

```{r}
over_identification <- 
  abs(scs$iiiii2 - 6) + abs(scs$iiiii6 - 6) + abs(scs$iiiii20 - 6) + abs(scs$iiiii24 - 6)
```

```{r}
hist(over_identification)
```



# Scala Multidimensional Scale of Perceived Social Support (MSPSS)

The MSPSS is a 12-item scale designed to measure perceived social support from three sources:

- Family, 
- Friends, 
- a Significant other

Let start with the coding of mspss. First, we select the right columns:
```{r}
mspss <- df %>% 
  select(X220:X231)
```

Then we change the column names to facilitate coding
```{r}
item_names <- paste0("iiiiii", 1:12)
names(mspss) <- item_names
```

## Family
```{r}
family <- 
  mspss$iiiiii3 + mspss$iiiiii4 + mspss$iiiiii8 + mspss$iiiiii11
```

```{r}
hist(family)
```

## Friends

```{r}
friends <- 
  mspss$iiiiii6 + mspss$iiiiii7 + mspss$iiiiii9 + mspss$iiiiii12
```

```{r}
hist(friends)
```

## A significant other

```{r}
significant_other <-
  mspss$iiiiii1 + mspss$iiiiii2 + mspss$iiiiii5 + mspss$iiiiii10
```

```{r}
hist(significant_other)
```




